---
title: "Calibration and Simulation"
author: "Christian Testa"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{Calibration and Simulation}
    %\VignetteEngine{knitr::rmarkdown}
    \usepackage[utf8]{inputenc}
---

This vignette is a guide to using the gc-regional package to create predictions
for the prevalence of gonorrhea in Baltimore or San Francisco.

First, we need to install. 
Since the package is hosted in a private repository on the PPML team's organization page, 
installation through devtools' install_github command requires an additional argument:
`auth_token`, which can be retrieved from GitHub. 

```{r, eval=FALSE}
devtools::install_github("ppml/gc-regional",
                         ref = "R-package",
                         auth_token = insert_auth_token_in_quotes_here)
```

Now we can load the package.
```{r}
library(gcRegional)
```

The next step is to load the parameters necessary for the desired site. 
To do this we run the `load_start()` function, which can be passed
the parameter `site`, or if `site` is missing as an argument the function 
will ask the user to enter the site. 

```{r}
load_start(site = "BA")
# OR
# load_start(site = "SF")
```

Let's go ahead and retrieve our vector of initial starting parameter values, `theta`,
the vector of standard deviations for each of our prior distributions, `sd.prior`, 
and then let's run Monte Carlo Markov Chain inference to learn posterior distributions
for each of our model parameters. 

```{r, R.options=list(max.print=10)}
#########################################
### to run/check the calibration code ###
#########################################

# dLogPosterior is the target required by the myMCMC function in the fitR
# package, init.theta=starting values of parameters, proposal.sd = initial guess
# for SD of parameters, n.iterations = number of iterations to run MCMC for

theta <- gc_env$theta
sd.prior <- gc_env$sd.prior
mcmc_test<-my_mcmc(target = dLogPosterior, init.theta = theta, proposal.sd = sd.prior/100, n.iterations = 10)
```


The following code block demonstrates how we can save data from our Monte Carlo
Markov Chain (MCMC) parameter inference algorithm.
```{r}
# Optionally the output_directory below can be replaced with a more accessible
# location, like "~/Documents/gcRegional_outputs" or something similar.
output_directory <- file.path(tempdir(), "gcRegional_outputs")
if (!dir.exists(output_directory)) dir.create(output_directory)
test_filepath = file.path(output_directory, paste("mcmc_test", Sys.time()))
save(mcmc_test, file=test_filepath)
print(test_filepath)
```


If running diagnostics or analysis on the saved MCMC data, make sure the correct
site parameters are loaded into the environment by running load_start with the
site matching the saved data.
```{r, echo=FALSE}
library(ggplot2) 
library(grid)
library(gridExtra)
library(reshape2)
```
```{r, R.options=list(max.print=10)}
site_in_filepath <- ifelse(grepl("BA", test_filepath), "BA", "SF")
if (gc_env$site != site_in_filepath) load_start(site_in_filepath)

x <- load(test_filepath)
mcmc_test <- get(x); rm(x)

my_trace<-coda::mcmc(mcmc_test$trace)

1-coda::rejectionRate(my_trace)
lattice::xyplot(my_trace[, 1:10])
trace.burn <- fitR::burnAndThin(my_trace, burn=4)
trace.burn.thin <- fitR::burnAndThin(my_trace, thin=60)

post.sample <- model_fits(trace.burn, sample.size=100)
pred <- as.data.frame(post.sample$outputs)
gc_assign(pred)
theta.list <- as.data.frame(post.sample$theta.list)
plot_posteriors(output_directory = output_directory)

```
