---
title: Implementing Model Structure Variations
---

This document is a (working draft) explanation of the variations 
to the gcRegional model which are implemented through a `gc_testing` parameter. 

To calibrate the model using one of the following variations, one simply uses the 
workflow

```{r eval=F}
library(gcRegional)
gc_testing <- c('logistic_screening')
calibrate_gcRegional(...)
```

## `use_national_posterior_means`

To use the `national_posterior_means` variation of the model, 
the `gc_testing` object should be a list which contains a 
character vector called `national_posterior_means` which specifies
the names of the values which should be taken from the means of 
the national model's posterior distribution.

For example, the first variation with fixing variables to the means
of components in the national posterior distribution looked like this:
```{r, eval=F}
gc_testing <- list(use_national_posterior_means = c(
  "log.rr.screen.m3",
  "log.rr.screen.f3",
  "log.rr.screen.ac",
  "log.c.min.m.1",
  "log.c.min.m.2",
  "log.c.min.f.1",
  "log.c.min.f.2",
  "log.c.min.msm.1",
  "log.c.min.msm.2",
  "log.dur.inf.symp.m",
  "log.dur.inf.symp.msm",
  "log.dur.inf.symp.f",
  "log.dur.inf.asymp.m",
  "log.dur.inf.asymp.f",
  "log.dur.inf.asymp.msm",
  "logit.b.m",
  "logit.b.f",
  "logit.b.msm",
  "logit.symp.m",
  "logit.symp.f",
  "logit.symp.msm" 
))
```

Note that arbitrary subsets of the `theta` vector may be included in the 
`use_national_posterior_means` character vector within the `gc_testing` 
as long as they are elements of the `inst/extdata/national_posterior_means.rds` file
inside the gcRegional package.

## `logistic_screening`

In order to implement `logistic_screening` as a variation which can be turned on 
using `gc_testing` I've added the following code in various places within the gcRegional project. 

#### a boolean test for if `logistic_screening` is on in `gc_testing.R`
```{r eval=F}
logistic_screening_variation <- function() {
  if (exists('gc_testing', envir=.GlobalEnv) &&
      'logistic_screening' %in% gc_testing) {
    TRUE
  } else FALSE
}
```

#### add logistic growth parameters to the prior in `calibration.R`
```{r eval=F}
if (logistic_screening_variation()) {
  screening_names <- c(
    "m1.1", "m2.1", "m1", "m2", "m1", "m2", 'msm1', 'msm2', "f1.1", "f2.1", "f1", "f2", "f1", "f2")
  for (scr_name in screening_names) {
    theta[paste0('log.', scr_name, '.growth')] <- log(0.2)
    sd.prior[length(sd.prior)+1] <- sqrt(2/9)
  }
  gc_env$screening_names <- screening_names
  theta['log.rep.symp.growth'] <- log(0.2)
  sd.prior[length(sd.prior)+1] <- sqrt(2/9)
}
```

This adds terms like `theta['log.m1.1.growth']` to the `theta` parameter vector so that 
each of the screening curves' logistic growth rate are individually controlled in calibration.

This also adds a growth rate for the reporting probability for symptomatic cases.

#### an optional term in the prior product expression in `prior.R`
```{r eval=F}
# rest of the prior * 
( if (logistic_screening_variation()) {
  prod(
    dgamma(
    x = sapply(gc_env$screening_names, function(x) {
    exp(theta[paste0('log.', x, '.growth')])
    })
    ,shape = 2
    ,rate = 3
    )
  ) *
  dgamma(exp(theta['log.rep.symp.growth']), 2, 3)
} else 1
)
```
Note that this defaults to 1 if we aren't in the `logistic_screening_variation()`.

This arbitrarily assumes that `shape1=2` and `shape2=5` are good prior parameters for 
our logistic growth curves. 

The growth parameter in principle is a positive valued number with no upper limit, so I wanted it to be
able to go up to values around 2, and since a beta distribution is only valued on [0,1] I chose to use
a gamma distribution.

```{r echo=F}
x=seq(0, 2, 0.001)
df = data.frame(x=x, y=dgamma(x, 2, 3))
library(ggplot2)
print(ggplot(df, aes(x,y)) + geom_line() + geom_ribbon(aes(ymax=y, ymin=0), fill='steelblue1', alpha=0.4) + 
        ggtitle("dgamma(x, 2, 3)"))
```

There is a small amount of reasoning behind this distribution: 
If the growth rate is around 1 or greater then the distribution practically becomes a step function: 

```{r echo=F}
library(gcRegional)
x = seq(0, 16, 0.1)
y = logistic_growth(0.5, 0.8, 2, x)
df = data.frame(x,y)
print(ggplot(df, aes(x=x,y=y)) + 
        geom_line() + 
        xlab("years") + 
        ggtitle("logistic growth from .5 to .8 with growth rate 2", subtitle = "almost a step function"))
```

And on the other hand if the growth rate is very close to 0, the function becomes practically linear.

```{r echo=F}
library(gcRegional)
x = seq(0, 16, 0.1)
y = logistic_growth(0.5, 0.8, .05, x)
df = data.frame(x,y)
print(ggplot(df, aes(x=x,y=y)) + 
        geom_line() + 
        xlab("years") + 
        ggtitle("logistic growth from .5 to .8 with growth rate .05", subtitle = "almost linear"))
```

The standard deviation of the Gamma distribution with parameters α and β is 
$\sigma = \sqrt{\text{Var}} = \sqrt{\alpha / \beta^2} = \sqrt{2/9}$. This justifies
the terms added to `sd.prior` in the `calibration.R` file mentioned above.

#### construct screening matrix in `model_pred_function.R`
```{r eval=F}
if (logistic_screening_variation()) {
  screening <-
    matrix(
      sapply(gc_env$screening_names, function(x) {
        c(ilogit(theta[paste0('logit.screen.', x, '.a')]),
          ilogit(theta[paste0('logit.screen.', x, '.d')]),
          exp(theta[paste0('log.', x, '.growth')])
      )
    }), ncol=3, byrow=T)
  t_vec <-seq(0,1, length.out=(gc_env$cal.period+1))
  screen_mat <- apply(screening, 1, function(x) logistic_growth(x[[1]], x[[2]], x[[3]], t_vec))
}
```

#### construct reporting probability matrix in `model_pred_function.R`

```{r eval=F}
if (logistic_screening_variation()) {
  t_vec <-seq(0,16, length.out=(gc_env$cal.period+1))
  rep.trend <-
    matrix(rep(c(
      ilogit(theta['logit.rep.symp.a']), 
      ilogit(theta['logit.rep.symp.d']), 
      exp(theta['log.rep.symp.growth'])), 32), 
      ncol = 3, byrow = T)
  rep.trend <- apply(rep.trend, 1, function(x) {
    logistic_growth(x[[1]], x[[2]], x[[3]], t_vec)
    })
}
```
