---
title: "Plotting Prevalence"
author: "Christian Testa"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{Plotting Prevalence}
    %\VignetteEngine{knitr::rmarkdown}
    \usepackage[utf8]{inputenc}
---

This vignette is here to help standardize our procedure for plotting
prevalence related outputs from model calibrations and simulations. This
document serves as a template that can be saved separately and modified to work
with different calibrations.

First, let's specify some calibration data.
```{r}
library(gcRegional)
site <- "SF"
load_start(site)

# Replace this calibration filepath when using different calibration outputs
# (and update the site variable). Calibration outputs should be the output of the
# gcRegional::my_mcmc method.
calibration_filepath <-
  system.file(package = "gcRegional",
  "data",
  "gc_regional_test_all_SF_2017-09-12 22:16:10")


# Load the calibration file data
x <- load(calibration_file)

# Rename the calibration data to mcmc_test
calibration <- get(x); rm(x)

trace <- calibration$trace
rm(calibration)

# burnin
burnin <- 100
trace <- trace[burnin+1:nrow(trace), ]

# sample
sample_size <- 100
trace <- dplyr::sample_n(trace, sample_size)

```

Inside the `prevalence_plotting.R` source code file, there two functions which
generate prevalence data that we are interested in visualizing:
`tidy_prevalence_by_demographic` and `tidy_prevalence_dfs_for_many_simulations`.

See the documentation `?tidy_prevalence_by_demographic` and
`?tidy_prevalence_dfs_for_many_simulations` for further explanation of what
these functions do.

At a high level, these functions provide an interface to run simulations based
on calibration data and then tabulate the number of infected in specified
subpopulations in those simulations.

**Todo:** I think I should change the `relative` parameter to something like
`mode` which can be specified as one of several options: `'numberinfected'`,
`'percentoftotalinfections'`, or `'prevalenceinsubpopulation'`. At the moment, 
`relative=F` corresponds to what I'm calling `'numberinfected'`, and 
`relative=T` corresponds to `'percentoftotalinfections'`. 

**Todo:** I also think that these functions need to be drawing from the 
calibration *after* burn-in. However, at this point in time I don't think
we've conclusively decided how long the burn-in period should be.

## Number of Infected

First, we will go through examples of plotting the numbers of infected 
individuals in each subpopulation. 

```{r}
prevalence_dataframes <- tidy_prevalence_dfs_for_many_simulations(
  trace_sample = trace,
  ijkl_subset = c('i', 'j'),
  relative = F
)
```

Since the data generated above is in a list format, we either need to 
average the dataframes together or merge them into one long dataframe
to visualize their contents. 

#### Merging and Visualizing Each Simulation
```{r}
prevalence_data_all <- do.call(rbind, prevalence_dataframes)
g <- plot_faceted_prevalence(prevalence_dfs = prevalence_data_all,
                             site = gc_env$site,
                             relative = F)
print(g)
```

The `plot_faceted_prevalence` function also has a scales parameter which
is passed to the facet_wrap function so that we can see each population
on separate y-axes if we'd like.
```{r}
g <- plot_faceted_prevalence(prevalence_dfs = prevalence_data_all,
                             site = gc_env$site,
                             scales = "free_y",
                             relative = F)
print(g)
```

#### Averaging and Visualizing Stacked Population Trends
```{r}
prevalence_data_avg <- average_tidy_prevalence_dfs(prevalence_dataframes)
g <- plot_stacked_area_prevalence(avg_prevalence = prevalence_data_avg,
                                  site = gc_env$site,
                                  relative = F)
print(g)
```

## Percent of Total Infections

Now we will go through the same procedures but with slightly different
arguments to produce plots which show the percentage of total infections
that are experienced by each subpopulation in the simulated data.

```{r}
prevalence_dataframes <- tidy_prevalence_dfs_for_many_simulations(
  trace_sample = trace,
  ijkl_subset = c('i', 'j'),
  relative = T
)

prevalence_data_all <- do.call(rbind, prevalence_dataframes)
g <- plot_faceted_prevalence(prevalence_dfs = prevalence_data_all,
                             site = gc_env$site,
                             relative = T)
print(g)

prevalence_data_all <- do.call(rbind, prevalence_dataframes)
g <- plot_faceted_prevalence(prevalence_dfs = prevalence_data_all,
                             site = gc_env$site,
                             relative = T,
                             scales = "free_y")
print(g)

prevalence_data_avg <- average_tidy_prevalence_dfs(prevalence_dataframes)
g <- plot_stacked_area_prevalence(avg_prevalence = prevalence_data_avg,
                                  site = gc_env$site,
                                  relative = T)
print(g)
```
