---
title: "Prevalence Outcomes"
author: "Christian Testa"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{Prevalence Outcomes}
    %\VignetteEngine{knitr::rmarkdown}
    \usepackage[utf8]{inputenc}
---

This vignette will serve the purpose of standardizing our methodology
for producing prevalence outcomes from the gcRegional model. 

gcRegional uses MCMC to produce a distribution on the set of parameters that
serve as input into the compartmental model of gonorrhea. This distribution is
calibrated by MCMC to reflect the likelihood of given parameter values producing
the observed data. To visualize the outcomes of this calibration, we sample from
the posterior distribution to and simulate the outcomes of those choices of
parameter values.

The model is calibrated to observed data in the time period 2010-2016, after 
which we employ several intervention scenarios to simulate how changes in 
parameters which control the screening rates of specific populations affect
the prevalence of gonorrhea in the models simulation of the 2017-2021 time
period. 

### Preparing Infection Data

Before we can visualize the prevalence of the model, we have to collect
data from model simulations varying the screening interventions and storing 
the number infected in each compartment and the compartment size in each 
year. 

For each site, we will construct a dataframe with the columns:

- intervention.id
- simulation
- population.id
- year
- n.infected
- population.size

First, let's get a calibration file to work with:

```{r get calibration filepath}
library(dplyr)

# Get the most recent calibration file for site = "SF" or "BA"
get_calibration_filepath <- function(site) {
  calibration_file <-
    system.file("data", package = 'gcRegional') %>%
    list.files(full.names = T) %>%
    grep(site, ., value=T) %>%
    last
  return(calibration_file)
}
```

Next, we need to sample a set of parameter-vectors from the calibration.

```{r sample theta}
# Sample sample_size number of theta_values from the trace of the calibration.
sample_calibration_trace <- function(
  calibration_filepath,
  burnin = 100,
  sample_size = 100) {
  
  x <- load(calibration_filepath) # load data; return name of object
  calibration <- get(x) # rename object -> "calibration"
  trace <- calibration$trace # extract theta values as trace dataframe
  trace <- trace[(burnin+1):nrow(trace), ] # 
  trace_sample <- dplyr::sample_n(trace, sample_size) %>%
    as.data.frame
  return(trace_sample)
}
```

Now I want to be able to count the number of infected individuals from each
population given a vector of parameters.

```{r simulate and record data}
calculate_n_infected <- function(
  theta,
  years = 2010:2016,
  interv = "base_case") {

  prediction_epi(theta, interv) # run model simulation
  sol <- gc_env$sol # record simulation output
  year_rows <- years - 1941 # adjust years to match row-indices of output
  y.index <- gc_env$y.index[1:28] # symptomatic infected
  z.index <- gc_env$z.index[1:28] # asymptomatic infected
  s.index <- gc_env$s.index[1:28] # susceptible, not-infected
  nsa.index <- gc_env$nsa.index[1:28] # not sexually active

  if (! all(year_rows %in% 1:nrow(sol))) # check that years are within simulation
    stop("The specified years aren't within the range of the simulated data.
    The values gc_env$cal.end and gc_env$model.end probably need to be updated.")

  # sum number infected per population
  n_infected <- sol[year_rows, 1+y.index] + sol[year_rows, 1+z.index]
  # sum total population sizes
  population_size <- n_infected + sol[year_rows, 1+s.index] + sol[year_rows, 1+nsa.index]

  # Rename rows/columns properly
  colnames(n_infected) <- 1:28
  rownames(n_infected) <- years
  colnames(population_size) <- 1:28
  rownames(population_size) <- years

  # Reshape n_infected
  n_infected <- reshape2::melt(
    n_infected,
    varnames = c("year", "population.id"),
    value.name = "n.infected")

  # Reshape population_size
  population_size <- reshape2::melt(
    population_size,
    varnames = c("year", "population.id"),
    value.name = "population.size")

  # Since n_infected and population_size were constructed with methods that will
  # ensure their populations and years are in the same order, we can now take
  # the population.size column and insert it into n_infected (or vice-versa) and
  # return this as our output.
  n_infected[['population.size']] <- population_size[['population.size']]
  return(n_infected)
}
```

Now that we have `calculate_n_infected`, we can run many simulations for each
given intervention. 

```{r collect many simulation results}
collect_many_simulations_results <- function(
  trace_sample,
  years = 2010:2016,
  interv = "base_case") {

  result <- list()
  for (i in 1:nrow(trace_sample)) {
    # Get trace_sample[i, ] with correct names
    theta <- setNames(as.numeric(trace_sample[i, ]), colnames(trace_sample))
    # Save simulation results
    result[[length(result)+1]] <- 
      calculate_n_infected(theta, years = years, interv = interv)
    # Add a simulation number column
    result[[length(result)]][['simulation.n']] <- i
  }
  
  # Concatenate each simulation's data and return
  result <- do.call(rbind, result)
  return(result)
}
```

To save on file size, I will record simulation data from the
base-case in the years 2010-2021 while for all other interventions I will record
data only from 2017-2021 because the interventions start in 2016 and do not
change the simulation results in the 2010-2016 period.

To defend the claim that the 2010-2016 period data is the same regardless of 
the intervention specified, we can check for a given vector of parameters that
the simulation results are the same.

```{r check preintervention equality}
load_start("SF")
intervention_ids <- names(gc_env$intervention_names)
preintervention_period_is_unaffected <- length(unique(
  lapply(intervention_ids, function(id) {
    calculate_n_infected(theta = gc_env$theta, interv = id)
  }))) == 1
if (preintervention_period_is_unaffected) 
  cat("Simulation results in the years 2010:2016 are consistently equal, 
      independent of the intervention specified.")
```


Let's go ahead and collect data for each intervention. 

```{r collect intervention data}
simulate_intervention_results <- function(trace_sample) {
  
  gc_env$cal.end <- 80 # End of calibration period cpp 0 indexing
  gc_env$model.end <- 81
  
  intervention_ids = c(
    "base_case",
    "high_activity_young_annual",
    "high_activity_young_semi_annual",
    "high_activity_young_quarter_annual",
    "young_annual",
    "young_semi_annual",
    "young_quarter_annual",
    "high_activity_MSM_annual",
    "high_activity_MSM_semi_annual",
    "high_activity_MSM_quarter_annual",
    "MSM_annual",
    "MSM_semi_annual",
    "MSM_quarter_annual",
    "high_activity_annual",
    "high_activity_semi_annual",
    "high_activity_quarter_annual",
    "female_young_annual",
    "female_young_semi_annual",
    "female_young_quarter_annual"
    )

  result <- list()
  
  for (id in intervention_ids) {
    # Set the years to be recorded according to the intervention
    if (id == "1") years <- 2010:2021
    else years <- 2017:2021
    
    # Record simulation results
    result[[length(result)+1]] <- 
      collect_many_simulations_results(
        trace_sample = trace_sample,
        years = years,
        interv = id)
    
    # Add an intervention.id column
    result[[length(result)]][['intervention.id']] <- id
  }
  
  result <- do.call(rbind, result) %>% as.data.frame(., stringsAsFactors=FALSE)
  
  return(result)
}
```


```{r generate data}
simulate_intervention_results_at_both_sites <- function() {
  results <- list()
  for (site in c("SF", "BA")) {
    load_start(site)
    calibration_filepath <- get_calibration_filepath(site)
    trace_sample <- sample_calibration_trace(calibration_filepath = calibration_filepath)
    results[[site]] <- simulate_intervention_results(trace_sample)
    results[[site]][['site']] <- site
  }
  results <- do.call(rbind, results) %>% as.data.frame(., stringsAsFactors=FALSE)
  return(results)
}
```


Now we're finally in a position to evaluate the function's we've constructed, and 
we can store their results as a dataframe called `n_infected`. 
```{r evaluate functions and save data}
if (! exists("n_infected", where='package:gcRegional')) {
  
  n_infected <- simulate_intervention_results_at_both_sites()
  
  save(n_infected,
       file = paste0(
       "~/Documents/gc-regional/data/n_infected.rda"
       ))
}
```



### Manipulating Infection Data

Since our model has 32 populations (which each have (symptomatic and
asymptomatic) infected and susceptible individuals), in order to simplify the
plots of prevalence/infections and other outputs we will need to be able to
combine populations together (i.e. the old black and young black can be combined
to form the Black population).

```{r group populations}
# This function will take a list of dimensions, convert them to their 
# corresponding options with the popnames object, and then list the 
# indices of the populations within each group. 

group_populations <- function(
  free_dims = c('demographic', 'sex', 'risk', 'age'),
  fixed_dims = c()) {
  
  dim_ids <- c(
    demographic = 'i',
    sex = 'j',
    risk = 'k',
    age = 'l'
  )
  
  dim_options <- list()
  for (dim in free_dims) {
    dim_options[[length(dim_options)+1]] <- 
      gc_env$popnames[[dim_ids[[dim]]]]
  }
  for (dim in fixed_dims) {
    dim_options[[length(dim_options)+1]] <-
      dim
  }
  
  dim_combinations <- purrr::cross(dim_options)
  dim_combinations <- lapply(dim_combinations, as.character)
  
  groups <- list()
  for (i in 1:length(dim_combinations)) {
    groups[[paste(dim_combinations[[i]], collapse = " ")]] <-
      pop_names_to_index(dim_combinations[[i]])
  }
  return(groups)
}
```

Additionally, rather than having many simulations for every single year, we 
would rather have mean values with 95% confidence intervals surrounding the
mean-values in each year. 

```{r calculating confidence}
calculating_confidence <- function(n_infected, varname = 'n.infected', confidence = 0.95) {
  
  lower_bound <- (1 - confidence) / 2
  upper_bound <- confidence + (1 - confidence) / 2
  
  results <- list()
  for (individual_year in unique(n_infected$year)) {
    for (interv in unique(n_infected$intervention.id)) {
      for (individual_site in unique(n_infected$site)) {
        for (pop in unique(n_infected$population.id)) {
        
          filtered_df <-
            filter(n_infected,
            year == individual_year,
            population.id == pop,
            site == individual_site,
            intervention.id == interv)
          
          if (nrow(filtered_df) > 0) {
            mean <- mean(filtered_df[[varname]], na.rm = T)
            ci_high <- quantile(filtered_df[[varname]], upper_bound, na.rm = T)
            ci_low <- quantile(filtered_df[[varname]], lower_bound, na.rm = T)
            population.size <- mean(filtered_df[['population.size']], na.rm = T)
            
            results[[length(results)+1]] <- c(
              year = individual_year,
              intervention.id = interv,
              site = individual_site,
              population.id = pop,
              mean = mean,
              ci_high = ci_high,
              ci_low = ci_low,
              population.size = population.size
            )
          }
        }
      }
    }
  }
  
  results <- do.call(rbind, results) %>% as.data.frame(., stringsAsFactors=FALSE)
  return(results)
}
```

Let's go ahead and save some confidence data so that this vignette doesn't have
to calculate the confidence every time it renders. 

```{r saving confidence}
if (! exists('n_infected_confidence', where = 'package:gcRegional')) {
  n_infected_confidence <- calculating_confidence(n_infected, varname = 'n.infected')
  save(n_infected_confidence, file="~/Documents/gc-regional/data/n_infected_confidence.rda")
}
```

Now that we can group the populations and we have our mean-values for 
cases and prevalence with confidence intervals, we will want to be able
to regroup the populations and sum their mean case counts, prevalence rates,
and those values' confidence intervals.

```{r combining populations into groups with confidence}

combine_populations_with_confidence <- function(
  df,
  grouping = group_populations()
) {
  
  results <- list()
  for (sitex in unique(df$site)) {
    for (interv in unique(df$intervention.id)) {
      for (yearx in unique(df$year)) {
        for (i in 1:length(grouping)) {
          group <- grouping[[i]]
          
          filtered_df <- filter(
            df,
            year == yearx,
            site == sitex,
            intervention.id == interv,
            population.id %in% group
          )
          
          if ( nrow(filtered_df) > 0 ) {
            meanx <- sum(as.numeric(filtered_df$mean))
            ci_high <- sum(as.numeric(filtered_df$`ci_high.97.5%`))
            ci_low <- sum(as.numeric(filtered_df$`ci_low.2.5%`))
            popsize <- sum(as.numeric(filtered_df$population.size))
            
            results[[length(results)+1]] <- 
              list(
                year = yearx, 
                site = sitex,
                intervention.id = interv,
                population.name = names(grouping)[[i]],
                mean = meanx,
                ci_high = ci_high,
                ci_low = ci_low,
                population.size = popsize
              )
          }
        }
      }
    }
  }
  
  results <- do.call(rbind, results) %>% as.data.frame(., stringsAsFactors=F)
  return(results)
}


```

Since only the base case includes the data from the 2010:2016 period, we need
a function which will copy the base-case years into data that looks like 
another intervention for 2010:2016, and then group the populations together.

```{r prepare intervention data}
coerce_df_coltypes <- function(df, types) {
  typenames <- names(types)
  if (! is.null(typenames) && length(typenames) == length(types)) {
    if (! all(typenames %in% colnames(df))) stop("the names of types must be colnames of df.")
    for (i in seq(types)) {
      df[[typenames[[i]]]] <- as(df[[typenames[[i]]]], types[[i]])
    }
  } else {
    if (length(types) > ncol(df)) stop("the length of types must be less than ncol(df).")
    for (i in seq(types)) {
      type <- types[[i]]
      df[[i]] <- as(df[[i]], type)
    }
  }
  return(df)
}



prepare_intervention_data <- function(
  df,
  city = "SF",
  intervention = "1",
  years = 2010:2021,
  free_dimensions = c("demographic", "age", "sex", "risk"),
  fixed_dimensions = c()
) {
  
  # Filter our dataframe for only the intervention, site, and years 
  # we're interested in.
  filtered_df <- filter(
    df,
    site == city,
    year %in% years,
    intervention.id == intervention)
  
  # Since only the Base Case is saved for 2010:2016, if any of the 
  # years of interest are in 2010:2016, grab those separately and 
  # add them to the filtered_df. 
  if (intervention != "1") {
    base_case_years <- dplyr::intersect(2000:2016, years)
    if ( length(base_case_years) > 0 ) {
      base_case_df <- filter(
        df,
        site == city,
        year %in% base_case_years,
        intervention.id == "1")
      base_case_df[['intervention.id']] <- intervention
      filtered_df <- rbind(base_case_df, filtered_df, stringsAsFactors=F) %>% 
        as.data.frame
    }
  }
  
  # Index the groups
  grouping <- group_populations(free_dims = free_dimensions,
                                fixed_dims = fixed_dimensions)
    
  # Group and sum the data
  filtered_df <- combine_populations_with_confidence(filtered_df, grouping = grouping)
  
  # Remove Female MSM
  female_msm_rows <-
    which(sapply(filtered_df[['population.name']], function(x)
    grepl('Female', x) && grepl('MSM', x)))
  if (length(female_msm_rows) > 0)
    filtered_df <- filtered_df[-female_msm_rows, ]
  
  # filtered_df$population.name <- as.character(filtered_df$population.name)
  # filtered_df$intervention.id <- as.character(filtered_df$intervention.id)
  # filtered_df$mean <- as.numeric(filtered_df$mean)
  # filtered_df$year <- as.integer(filtered_df$year)
  # filtered_df$`ci_high` <- as.numeric(filtered_df$`ci_high`)
  # filtered_df$`ci_low` <- as.numeric(filtered_df$`ci_low`)
  # filtered_df$population.size <- as.numeric(filtered_df$population.size)
  
  filtered_df <- coerce_df_coltypes(filtered_df, 
                                    c(year = 'integer', 
                                      mean = 'numeric',
                                      population.name = 'character',
                                      intervention.id = 'integer',
                                      ci_high = 'numeric',
                                      ci_low = 'numeric',
                                      population.size = 'numeric'))
  
  return(filtered_df)
}
```


### Visualizing Infection Data

Now we can go ahead and make the most basic of visualizations: A specific
intervention, visualized in either city, for a specific range of years,
with a specified population grouping. 

```{r some plots}
library(ggplot2)

make_intervention_plot <- function(
  cases_or_prevalence = 'cases',
  site = "SF",
  years = 2010:2016,
  intervention = "1",
  free_dimensions = c("demographic", "sex"),
  fixed_dimensions = c()) {
  
  if (! cases_or_prevalence %in% c('cases', 'prevalence')) 
    stop("cases_or_prevalence argument must be either 'cases' or 'prevalence'.")
  
  site_names <- c(
    "SF" = "San Francisco",
    "BA" = "Baltimore")
  
  intervention_names <- c(
    '1' = "Base Case",
    "2b" = "Focused Young - Annual Screening",
    "2a" = "Focused Young - Semi-Annual Screening",
    "3a" = "Focused Young - Quarter-Annual Screening",
    "4a" = "All High Risk - Annual Screening",
    "5a" = "Focused MSM - Semi-Annual Screening",
    "6a" = "Focused MSM - Quarter-Annual Screening",
    "7" = "All MSM - Annual Screening",
    "8" = "All MSM - Semi-Annual Screening",
    "9" = "All MSM - Quarter-Annual Screening"
  )
  
  df <- get("n_infected_confidence")
  
  df <- prepare_intervention_data(
    df = df, city = site, intervention = intervention, 
    years = years,
    free_dimensions = free_dimensions,
    fixed_dimensions = fixed_dimensions)
  
  if (cases_or_prevalence == 'prevalence') {
    df$mean <- df$mean / df$population.size * 100
    df$ci_high <- df$ci_high / df$population.size * 100
    df$ci_low <- df$ci_low / df$population.size * 100
  }
  
  g <- ggplot(df, aes(x=year, y=mean, color=population.name)) + 
    geom_line() + 
    geom_ribbon(aes(ymin = ci_low, ymax=ci_high, fill=population.name), color=NA, alpha=0.3) + 
    ggtitle(paste0(
      ifelse(cases_or_prevalence == 'cases',
             'Number of Cases in ',
             'Prevalence rates in '),
      site_names[[site]],
      " - ",
      intervention_names[[intervention]])) + 
    ylab(ifelse(cases_or_prevalence == 'cases',
                'Number of Infections', 'Prevalence %'))
  
  return(g)
}



# df <- prepare_intervention_data(
#   df = n_infected_confidence, city = "BA", intervention = '1',
#   fixed_dimensions = c(demographic="Black", age="Young", sex="Female"))
# 
# ggplot(df, aes(x=year, y=mean / population.size, color=population.name)) + 
#   geom_line() + 
#   geom_ribbon(aes(ymin = ci_low / population.size, ymax=ci_high / population.size, fill=population.name), color=NA, alpha=0.3) + 
#   ggtitle("Number of Cases in Baltimore - Base Case Scenario")



# make_intervention_plot(site = "BA", cases_or_prevalence = "prevalence",
#                        intervention = '1',
#                        years = 2000:2021,
#                        free_dimensions = c(),
#                        fixed_dimensions = c(age='Young', demographic='Black', sex='Female'))
# 
# 
# make_intervention_plot(site = "SF", cases_or_prevalence = "prevalence",
#                        intervention = '1',
#                        free_dimensions = c('demographic', 'age'),
#                        fixed_dimensions = c())
# 
# 
# make_intervention_plot(site = "BA", cases_or_prevalence = "prevalence",
#                        intervention = '1',
#                        free_dimensions = c('risk', 'age'),
#                        fixed_dimensions = c('Black'))

library(ggplot2)

g <- make_intervention_plot(site = "BA", cases_or_prevalence = "prevalence",
                       intervention = 'base_case',
                       years = 2000:2021,
                       free_dimensions = c(),
                       fixed_dimensions = c(demographic='Black', sex='Female'))

h <- make_intervention_plot(site = "BA", cases_or_prevalence = "prevalence",
                       intervention = 'base_case',
                       years = 2000:2021,
                       free_dimensions = c(),
                       fixed_dimensions = c(demographic='MSM'))

i <- make_intervention_plot(site = "BA", cases_or_prevalence = "prevalence",
                       intervention = 'base_case',
                       years = 2000:2021,
                       free_dimensions = c(),
                       fixed_dimensions = c(demographic='Black', sex='Male'))


dat <- dplyr::bind_rows(g$data, h$data, i$data)


ggplot(dat, aes(x=year, y=mean, ymax=ci_high, ymin=ci_low, color=population.name)) + 
  geom_ribbon(aes(fill=population.name), color=NA, alpha=0.4) + 
  geom_line() + ylab("cases") + ggtitle("Prevalence in Baltimore") + 
  scale_x_continuous(name = 'year', 2000:2021) + theme(axis.text.x = element_text(angle=90))

```

