---
title: Figures Documentation
author: Christian Testa
output: 
    html_document:
        toc: true
---

# Figures

This document serves the purpose of showing where the figures available in the manuscript 
are available in this package and git repository. Additionally this document outlines 
the way in which each of these figures are produced using the `gcRegional` R package. 

The figures will be listed here as follows: 

- fig1 Fit to Diagnosis Rates
- fig2 Intervention Prevalence Time Trends
- fig3 Additional Tests and Infections Averted
- fig4 Infections Averted in LTFU scenarios
- calibration figures, BA and SF
- supplement fig1 Breakdown of Modeled Incidence and Reported Diagnoses
- supplement fig2 MSM Intervention Sensitivity Analysis

```{r, echo=T, results='hide', warning=FALSE}
devtools::load_all('.')
```

### fig1 Fit to Diagnosis Rates

### fig2 Intervention Prevalence Time Trends

```{r}
# .render_interventions_df()
# .render_intervention_prevalence_summary_df()
plots <- plot_intervention_prevalence_time_trends(save=T)
names(plots)
plots[['main_strategies_interventions_prevalence']]

# plots <- plot_intervention_prevalence_time_trends(bw=T, save=T)
# names(plots)
# plots[['main_strategies_interventions_prevalence']]
```

### fig3 Additional Tests and Infections Averted

##### Part A) Baltimore

```{r}
plots <- plot_number_needed_to_treat(save=T)
plots[['additional_tests_and_cases_averted_ba_hypothetical_all_activity']]
```

##### Part B) San Francisco

```{r}
plots[['additional_tests_and_cases_averted_sf_hypothetical_all_activity']]
```

### fig4 Infections Averted in LTFU scenarios

```{r}
plots[['cases_averted_ltfu']]
```

### supplement fig1 Breakdown of Modeled Incidence and Reported Diagnoses
```{r}
plot_comparison_of_model_incidence_and_diagnoses()
```

### supplement fig2 MSM Intervention Sensitivity Analysis

```{r}
plots <- plot_msm_interventions()
plots[['ba']]
plots[['sf']]
```

```{r}
interventions_msm <- readRDS(file.path(
  system.file(
    'intervention_analysis/',
    package = 'gcRegional'), 'interventions_msm.rds'))

ba_last_year <- filter(interventions_msm, site == 'BA') %>% `[[`('year') %>% max()
sf_last_year <- filter(interventions_msm, site == 'SF') %>% `[[`('year') %>% max()

interventions_msm %<>% filter((site == 'BA' & year == ba_last_year) | (site == 'SF' & year == sf_last_year))

interventions_msm %<>% mutate(
  interv = as.character(interv) %>% 
    recode(
      `MSM_1.5` = '1.5',
      `MSM_2.5` = '2.5',
      `MSM_3` = '3',
      `MSM_3.5` = '3.5',
      `MSM_4.5` = '4.5',
      `MSM_5` = '5',
      `MSM_annual` = '1',
      `MSM_quarter_annual` = '4',
      `MSM_semi_annual` = '2')) %>% 
  filter(interv != 'base_case')

interventions_msm_mean <- interventions_msm %>% 
  group_by(site, interv) %>% 
  summarize(
    mean_additional_tests = mean(additional_tests, na.rm=T),
    mean_cases_averted = mean(cases_averted, na.rm=T))


  make_plot <- function(site) { 
    site1 <- enquo(site)

    ggplot(filter(interventions_msm, site == !! site1, year == c(BA = ba_last_year, SF = sf_last_year)[[!! site]]), aes(x=additional_tests, y=cases_averted, color = interv)) + 
      geom_point(alpha=0.25) + 
      geom_point(data = filter(interventions_msm_mean, site == !! site1), mapping = aes(x = mean_additional_tests, y = mean_cases_averted, shape = 'Mean Outcomes by Intervention'), color = 'black') + 
      theme_minimal() + 
      labs(shape = 'Summary Statistics', x = 'Additional Tests', 
           y = 'Incident Infections Averted Compared to the Base Case',
           color = 'MSM Screening Frequency') +
      scale_shape_manual(values = c(`Mean Outcomes by Intervention` = 1)) + 
      scale_color_manual(values = scales::hue_pal()(n=length(unique(interventions_msm$interv))+1)[-1]) +
      expand_limits(x=0) + 
      scale_x_continuous(labels = function(x) format(x, scientific = FALSE)) + 
      ggtitle("Outcomes at the End of 5 Years of MSM Focused Interventions",
              subtitle = c(BA = "Baltimore", SF = "San Francisco")[[site]])
  }

  plots <- list()
  plots[['BA']] <- make_plot('BA')
  plots[['SF']] <- make_plot('SF')

  plots[['BA']]
  plots[['SF']]

```

### HR Targeting Sensitivity Analysis

```{r}_hr_complete
  interventions_df <- readRDS(
    file.path(
    system.file('intervention_analysis', package='gcRegional'),
    'interventions.rds'))
  
  intervention_sensitivity_df_ba <- readRDS(
    file.path(
    system.file('intervention_analysis/', package='gcRegional'),
    'interventions_data_mobile_outreach_sensitivity_BA.rds'))
  
  intervention_sensitivity_df_sf <- readRDS(
    file.path(
    system.file('intervention_analysis/', package='gcRegional'),
    'interventions_data_mobile_outreach_sensitivity_SF.rds'))
  
  interventions_df %<>% filter(interv %in% c('base_case', '1year_high_activity_semi_annual'))
  
  intervention_sensitivity_df <- 
    rbind.data.frame(
      interventions_df,
      cbind.data.frame(site = 'SF', intervention_sensitivity_df_sf),
      cbind.data.frame(site = 'BA', intervention_sensitivity_df_ba))
 
   intervention_sensitivity_df$year <- ifelse(intervention_sensitivity_df$year %% 1 < .25, intervention_sensitivity_df$year - intervention_sensitivity_df$year%%1, intervention_sensitivity_df$year)
   intervention_sensitivity_df$site <- as.character(intervention_sensitivity_df$site)
   intervention_sensitivity_df$interv <- as.character(intervention_sensitivity_df$interv)
   intervention_sensitivity_df$population <- as.character(intervention_sensitivity_df$population)
  
  saveRDS(intervention_sensitivity_df, file.path(
      system.file('intervention_analysis/', package='gcRegional'),
      'mobile_outreach_sensitivity_intervention_df.rds'))
 

intervention_sensitivity_df <- readRDS(file.path(
     system.file('intervention_analysis/', package='gcRegional'),
     'mobile_outreach_sensitivity_intervention_df.rds'))


.render_intervention_prevalence_summary_df_mobile_sensitivity <- function() { 

  df <- readRDS(system.file("intervention_analysis/mobile_outreach_sensitivity_intervention_df.rds", package='gcRegional'))

  .construct_interventions_description_df()

  int_prev_df <- df %>% 
    select(
      c(
        "site",
        "sim",
        "interv",
        "year",
        "population",
        "population_size",
        "symptomatic_cases",
        "asymptomatic_cases"
        )) %>% 
    filter(population == "All") %>% 
    select(-population) %>% 
    mutate(prevalence = (asymptomatic_cases + symptomatic_cases) / population_size) %>% 
    select(-c(population_size, asymptomatic_cases, symptomatic_cases))

  saveRDS(int_prev_df, file = file.path(
    system.file(
      package = 'gcRegional',
      "intervention_analysis/data/"
    ),
    'int_prev_sensitivity_df.rds'
  ))

  int_prev_ci_df <- group_by(int_prev_df, site, interv, year) %>% 
    summarise(mean = mean(prevalence, na.rm=T),
              ci_high = quantile(prevalence, 0.975, na.rm = T),
              ci_low = quantile(prevalence, 0.025, na.rm = T))

  last_int_prev_data_points <- as.data.frame(do.call(
    rbind.data.frame,
    list(
      filter(int_prev_ci_df, site == 'BA', year == 2022),
      filter(int_prev_ci_df, site == 'SF', year == 2021)
    )))

  int_prev_ci_df$site <-
    sapply(as.character(int_prev_ci_df$site), function(x)
    c(SF = 'San Francisco', BA = 'Baltimore')[[x]])

  last_int_prev_data_points$site <-
    sapply(as.character(last_int_prev_data_points$site), function(x)
    c(SF = 'San Francisco', BA = 'Baltimore')[[x]])

  int_prev_ci_df[int_prev_ci_df$site == 'San Francisco', 'year'] <- int_prev_ci_df[int_prev_ci_df$site == 'San Francisco', 'year'] - 2016
  int_prev_ci_df[int_prev_ci_df$site == 'Baltimore', 'year'] <- int_prev_ci_df[int_prev_ci_df$site == 'Baltimore', 'year'] - 2017

  int_prev_ci_df <- merge(int_prev_ci_df, intervention_descriptions, by.x = 'interv', by.y = 'shortnames', all.x = T)

  last_int_prev_data_points[last_int_prev_data_points$site == 'San Francisco', 'year'] <-
    last_int_prev_data_points[last_int_prev_data_points$site == 'San Francisco', 'year'] - 2016
  last_int_prev_data_points[last_int_prev_data_points$site == 'Baltimore', 'year'] <-
    last_int_prev_data_points[last_int_prev_data_points$site == 'Baltimore', 'year'] - 2017

  last_int_prev_data_points <- merge(last_int_prev_data_points, intervention_descriptions, by.x = 'interv', by.y = 'shortnames', all.x = T)
  last_int_prev_data_points$names <- ordered(last_int_prev_data_points$names, levels = rev(intervention_descriptions$names))

  # write.csv(x = last_int_prev_data_points, file = file.path(
  #   system.file(
  #     package = 'gcRegional',
  #     "intervention_analysis/data/"
  #   ),
  #   'prevalence_in_interventions_after_5_years.csv'
  # ))

  # write.csv(x = int_prev_ci_df, file = file.path(
  #   system.file(
  #     package = 'gcRegional',
  #     "intervention_analysis/data/"
  #   ),
  #   'prevalence_in_interventions_in_all_years.csv'
  # ))

  saveRDS(last_int_prev_data_points, file = file.path(
    system.file(
      package = 'gcRegional',
      "intervention_analysis/data/"
    ),
    'last_int_prev_data_points_mobile_sensitivity.rds'
  ))

  saveRDS(int_prev_ci_df, file = file.path(
    system.file(
      package = 'gcRegional',
      "intervention_analysis/data/"
    ),
    'int_prev_ci_df_mobile_sensitivity.rds'
  ))
}

.render_intervention_prevalence_summary_df_mobile_sensitivity()


#' Plot Time Trends of Prevalence in Interventions during the Intervention Time Period
#' 
#' 
plot_intervention_prevalence_time_trends_mobile_sensitivity <- function(save=F) { 

  require(ggrepel)
  
  .construct_interventions_description_df()

  last_int_prev_data_points <- 
  readRDS(file.path(
    system.file(
      package = 'gcRegional',
      "intervention_analysis/data/"
    ),
    'last_int_prev_data_points_mobile_sensitivity.rds'
  ))

  int_prev_ci_df <- readRDS(file.path(
    system.file(
      package = 'gcRegional',
      "intervention_analysis/data/"
    ),
    'int_prev_ci_df_mobile_sensitivity.rds'
  ))

  make_interventions_prevalence_plot <- function(interventions_list) {
    ggplot(
      filter(
      int_prev_ci_df,
      year >= 0,
      year <= 5,
      interv %in% interventions_list
      ),
      aes(x = year, y = 100 * mean, color = names)
      ) +
      geom_line() +
    facet_wrap(~site) + 
    scale_x_continuous(
      breaks = seq(0, 5, by = 1), 
      limits = c(0, 9)) +
    geom_label_repel(
      data = filter(last_int_prev_data_points, interv %in% interventions_list),
      aes(
      x = year,
      y = 100*mean,
      group = interv,
      label = names,
      # color = names,
      fill = names
      ),
      color = 'black',
      segment.color = 'black',
      segment.size = 0.1,
      segment.alpha = 0.8,
      # fontface = 'bold',
      alpha = 0.95,
      nudge_x = 2.5,
      direction = 'y',
      size = 2.5
      ) +
    expand_limits(y = 0) + 
    ylab("Prevalence (%)") +
    xlab("Years After Intervention Start") + 
    ggtitle("Prevalence Estimates During the Intervention Time Period") + 
    theme_bw() + 
    theme(legend.position = 'none') + 
    scale_color_manual(values = setNames(intervention_descriptions$color, intervention_descriptions$names)) + 
    scale_fill_manual(values = setNames(sapply(intervention_descriptions$color,
                                               colorspace::lighten, amount=.85),
                                        intervention_descriptions$names))
  }

  plots <- list()

  hypothetical_ints_high_activity <- hypothetical_interventions[grepl("high", hypothetical_interventions)]

  plots[['hypothetical_high_activity_interventions_prevalence']] <- make_interventions_prevalence_plot(c('base_case', '1year_high_activity_semi_annual',
    '1year_high_activity_semi_annual_lower_capture_rate',
    '1year_high_activity_semi_annual_complete_capture_rate'
    ))

  if (save) { 

    ggsave(file.path(
      system.file("intervention_analysis/figures/", package = 'gcRegional'),
      'intervention_prevalence_current_strategies.png'
      ),
      height = unit(5, 'in'),
      width = unit(9, 'in'),
      plot = plots[['current_strategies_interventions_prevalence']])
  } 

  return(plots)
}

plots <- plot_intervention_prevalence_time_trends_mobile_sensitivity()

plots[[1]]

# ggsave("~/Desktop/figure.png", width=7, height=4)
```


### Compare 1year Mobile Outreach HR/LR Sensitivity Analysis Outcomes

```{r}
# last_ba_year <- filter(intervention_sensitivity_df, site == 'BA') %>% `[[`('year') %>% max
# last_sf_year <- filter(intervention_sensitivity_df, site == 'SF') %>% `[[`('year') %>% max
# 
# 
# int_s_df <- intervention_sensitivity_df %>% 
#   filter(year == ifelse(site == 'SF', last_sf_year, last_ba_year), population == 'All') %>% 
#   select(-year)
# 
# make_additional_tests_plot <- function(site) { 
#   site1 <- site
#   site <- enquo(site)
#   ggplot(filter(int_s_df, site == !! site), aes(x = interv, group = sim, y = number_screened)) + 
#     geom_jitter(alpha=0.6, color = '#FDC086') + 
#     geom_boxplot(mapping = aes(group = interv), size = 1, alpha = 0.7, outlier.shape=NA) + 
#     theme_minimal() + 
#     coord_flip() + 
#     ggtitle('Number of Screening Tests in the Mobile Outreach Testing Sensitivity Analysis',
#     subtitle = c(SF = 'San Francisco', BA = 'Baltimore')[[site1]])
# }
# 
# make_additional_tests_plot('SF')
# 
# 
# make_add_tests_and_prevalent_infections_plot <- function(site) { 
#   site1 <- site
#   site <- enquo(site)
#   ggplot(filter(int_s_df, site == !! site), 
#          aes(x = number_screened, y = symptomatic_cases + asymptomatic_cases, color = interv)) + 
#     geom_point(aes(group = sim), alpha = 0.3) + 
#     geom_density_2d() + 
#     theme_minimal() + 
#     ggtitle('Additional Tests and Prevalent Infections', 
#     subtitle = c(SF = 'San Francisco', BA = 'Baltimore')[[site1]])
# }
# 
# make_add_tests_and_prevalent_infections_plot('SF')
# 
# library(plotly)
# plotly::ggplotly()
# 
# 
# make_prevalent_infections_and_incident_infections_plot <- function(site) { 
#   site1 <- site
#   site <- enquo(site)
#   ggplot(filter(int_s_df, site == !! site), 
#          aes(x = incident_cases, y = symptomatic_cases + asymptomatic_cases, color = interv)) + 
#     geom_point(aes(group = sim), alpha = 0.3) + 
#     geom_density_2d() + 
#     theme_minimal() + 
#     ggtitle('Incident Tests and Prevalent Infections', 
#     subtitle = c(SF = 'San Francisco', BA = 'Baltimore')[[site1]])
# }
# 
# make_prevalent_infections_and_incident_infections_plot('SF')
# 
# library(plotly)
# plotly::ggplotly()
```


### Let's look at a few more breakdowns of HR, LR in the 1year intervention

```{r}

  # interventions_df <- readRDS(
  #   file.path(
  #   system.file('intervention_analysis', package='gcRegional'),
  #   'interventions.rds'))
  
  intervention_sensitivity_df_ba <- readRDS(
    file.path(
    system.file('intervention_analysis/', package='gcRegional'),
    'interventions_data_mobile_outreach_sensitivity_BA_fixed.rds'))
  
  intervention_sensitivity_df_sf <- readRDS(
    file.path(
    system.file('intervention_analysis/', package='gcRegional'),
    'interventions_data_mobile_outreach_sensitivity_SF_fixed.rds'))
  
  # interventions_df %<>% filter(interv %in% c('base_case', '1year_high_activity_semi_annual'))
  
  intervention_sensitivity_df <- 
    rbind.data.frame(
      # interventions_df,
      cbind.data.frame(site = 'SF', intervention_sensitivity_df_sf),
      cbind.data.frame(site = 'BA', intervention_sensitivity_df_ba))

   # Format Years properly 
   intervention_sensitivity_df$year <- ifelse(intervention_sensitivity_df$year %% 1 < .25, intervention_sensitivity_df$year - intervention_sensitivity_df$year%%1, intervention_sensitivity_df$year)
   intervention_sensitivity_df$site <- as.character(intervention_sensitivity_df$site)
   intervention_sensitivity_df$interv <- as.character(intervention_sensitivity_df$interv)
   intervention_sensitivity_df$population <- as.character(intervention_sensitivity_df$population)
  
  saveRDS(intervention_sensitivity_df, file.path(
      system.file('intervention_analysis/', package='gcRegional'),
      'mobile_outreach_sensitivity_intervention_df3.rds'))
 

# intervention_df_2 <- readRDS(file.path(
#      system.file('intervention_analysis/', package='gcRegional'),
#      'mobile_outreach_sensitivity_intervention_df3.rds'))


.render_intervention_prevalence_summary_df_mobile_sensitivity2 <- function() { 

  df <- readRDS(system.file("intervention_analysis/mobile_outreach_sensitivity_intervention_df3.rds", package='gcRegional'))

  .construct_interventions_description_df()

  int_prev_df <- df %>% 
    select(
      c(
        "site",
        "sim",
        "interv",
        "year",
        "population",
        "population_size",
        "symptomatic_cases",
        "asymptomatic_cases"
        )) %>% 
    filter(population == "All") %>% 
    select(-population) %>% 
    mutate(prevalence = (asymptomatic_cases + symptomatic_cases) / population_size) %>% 
    select(-c(population_size, asymptomatic_cases, symptomatic_cases))

  saveRDS(int_prev_df, file = file.path(
    system.file(
      package = 'gcRegional',
      "intervention_analysis/data/"
    ),
    'int_prev_sensitivity_df3.rds'
  ))

  int_prev_ci_df <- group_by(int_prev_df, site, interv, year) %>% 
    summarise(mean = mean(prevalence, na.rm=T),
              ci_high = quantile(prevalence, 0.975, na.rm = T),
              ci_low = quantile(prevalence, 0.025, na.rm = T))

  last_int_prev_data_points <- as.data.frame(do.call(
    rbind.data.frame,
    list(
      filter(int_prev_ci_df, site == 'BA', year == 2022),
      filter(int_prev_ci_df, site == 'SF', year == 2021)
    )))

  int_prev_ci_df$site <-
    sapply(as.character(int_prev_ci_df$site), function(x)
    c(SF = 'San Francisco', BA = 'Baltimore')[[x]])

  last_int_prev_data_points$site <-
    sapply(as.character(last_int_prev_data_points$site), function(x)
    c(SF = 'San Francisco', BA = 'Baltimore')[[x]])

  int_prev_ci_df[int_prev_ci_df$site == 'San Francisco', 'year'] <- int_prev_ci_df[int_prev_ci_df$site == 'San Francisco', 'year'] - 2016
  int_prev_ci_df[int_prev_ci_df$site == 'Baltimore', 'year'] <- int_prev_ci_df[int_prev_ci_df$site == 'Baltimore', 'year'] - 2017

  int_prev_ci_df <- merge(int_prev_ci_df, intervention_descriptions, by.x = 'interv', by.y = 'shortnames', all.x = T)

  last_int_prev_data_points[last_int_prev_data_points$site == 'San Francisco', 'year'] <-
    last_int_prev_data_points[last_int_prev_data_points$site == 'San Francisco', 'year'] - 2016
  last_int_prev_data_points[last_int_prev_data_points$site == 'Baltimore', 'year'] <-
    last_int_prev_data_points[last_int_prev_data_points$site == 'Baltimore', 'year'] - 2017

  last_int_prev_data_points <- merge(last_int_prev_data_points, intervention_descriptions, by.x = 'interv', by.y = 'shortnames', all.x = T)
  # last_int_prev_data_points$names <- ordered(last_int_prev_data_points$names, levels = rev(intervention_descriptions$names))

  # write.csv(x = last_int_prev_data_points, file = file.path(
  #   system.file(
  #     package = 'gcRegional',
  #     "intervention_analysis/data/"
  #   ),
  #   'prevalence_in_interventions_after_5_years.csv'
  # ))

  # write.csv(x = int_prev_ci_df, file = file.path(
  #   system.file(
  #     package = 'gcRegional',
  #     "intervention_analysis/data/"
  #   ),
  #   'prevalence_in_interventions_in_all_years.csv'
  # ))

  saveRDS(last_int_prev_data_points, file = file.path(
    system.file(
      package = 'gcRegional',
      "intervention_analysis/data/"
    ),
    'last_int_prev_data_points_mobile_sensitivity3.rds'
  ))

  saveRDS(int_prev_ci_df, file = file.path(
    system.file(
      package = 'gcRegional',
      "intervention_analysis/data/"
    ),
    'int_prev_ci_df_mobile_sensitivity3.rds'
  ))
}

# .render_intervention_prevalence_summary_df_mobile_sensitivity2()


plot_intervention_prevalence_time_trends_mobile_sensitivity2 <- function(save=F) { 

  require(ggrepel)
  
  .construct_interventions_description_df()

  last_int_prev_data_points <- 
  readRDS(file.path(
    system.file(
      package = 'gcRegional',
      "intervention_analysis/data/"
    ),
    'last_int_prev_data_points_mobile_sensitivity3.rds'
  ))

  int_prev_ci_df <- readRDS(file.path(
    system.file(
      package = 'gcRegional',
      "intervention_analysis/data/"
    ),
    'int_prev_ci_df_mobile_sensitivity3.rds'
  ))

  make_interventions_prevalence_plot <- function(interventions_list) {
    ggplot(
      filter(
      int_prev_ci_df,
      year >= 0,
      year <= 5,
      interv %in% interventions_list
      ),
      aes(x = year, y = 100 * mean, color = names)
      ) +
      geom_line() +
    facet_wrap(~site) + 
    scale_x_continuous(
      breaks = seq(0, 5, by = 1), 
      limits = c(0, 9)) +
    geom_label_repel(
      data = filter(last_int_prev_data_points, interv %in% interventions_list),
      aes(
      x = year,
      y = 100*mean,
      group = interv,
      label = names,
      # color = names,
      fill = names
      ),
      color = 'black',
      segment.color = 'black',
      segment.size = 0.1,
      segment.alpha = 0.8,
      # fontface = 'bold',
      alpha = 0.95,
      nudge_x = 2.5,
      direction = 'y',
      size = 2.5
      ) +
    expand_limits(y = 0) + 
    ylab("Prevalence (%)") +
    xlab("Years After Intervention Start") + 
    ggtitle("Prevalence Estimates During the Intervention Time Period") + 
    theme_bw() + 
    theme(legend.position = 'none') + 
    scale_color_manual(values = setNames(intervention_descriptions$color, intervention_descriptions$names)) + 
    scale_fill_manual(values = setNames(sapply(intervention_descriptions$color,
                                               colorspace::lighten, amount=.85),
                                        intervention_descriptions$names))
  }

  plots <- list()

  hypothetical_ints_high_activity <- hypothetical_interventions[grepl("high", hypothetical_interventions)]

  plots[['mobile_outreach_sensitivity_interventions']] <- make_interventions_prevalence_plot(c('base_case', 
'1year_high_activity_semi_annual_2_10th_hr_pt133_lr',
'1year_high_activity_semi_annual_4_10th_hr_pt111_lr',
'1year_high_activity_semi_annual_5_10th_hr_pt1_lr'
)
    )

  if (save) { 

    ggsave(file.path(
      system.file("intervention_analysis/figures/", package = 'gcRegional'),
      'mobile_outreach_sensitivity_interventions.png'
      ),
      height = unit(5, 'in'),
      width = unit(12, 'in'),
      plot = plots[['mobile_outreach_sensitivity_interventions']])
  } 

  return(plots)
}

plots <- plot_intervention_prevalence_time_trends_mobile_sensitivity2(save=T)
plots[[1]]
```

### Boxplots with Jitter

```{r}
# load_all()

plots <- plot_number_needed_to_treat2(save=T)

plots[[1]]

```


### Additional Tables

Additional Tests, Incident Cases Averted for each Intervention
similar to Table 2


Mean with 95% CI of: 
  - Relative Reduction in Prevalence,
  - Relative Reduction in Cumulative Incident Infections, 
  - Relative Number of Additional Tests

By site and intervention

```{r}
# .render_intervention_summary_table <- function(site) { 
  require(data.table)

  df <- readRDS(system.file('intervention_analysis/interventions3.rds', package='gcRegional'))

  max_sf_year <- df %>% filter(site == 'SF') %>% `[[`('year') %>% max
  max_ba_year <- df %>% filter(site == 'BA') %>% `[[`('year') %>% max

  df %<>% mutate(
    year = ifelse(site == 'SF', year - max_sf_year + 5, year - max_ba_year + 5)) %>% 
  filter(year %in% c(0,5))

  df %<>% filter(population == 'All') 

  df2 <- df %>% 
    select(-population) %>% 
    mutate(prevalent_infections = symptomatic_cases + asymptomatic_cases) %>% 
    select(-c(symptomatic_cases, asymptomatic_cases)) %>% 
    select(-diagnosed_cases)

  basecase_df <- df2 %>% filter(interv == 'base_case') %>% select(-interv)

  df3 <- merge(df2, basecase_df, by = c('site', 'sim', 'year'), suffixes = c('', '.basecase'))

  df4 <- data.table::dcast(setDT(df3), site + sim + interv ~ year,
    value.var =  colnames(df3)[5:ncol(df3)])


   df5 <- 
     df4 %>% 
     mutate(
       number_screened = number_screened_5,# - number_screened_0,
       number_screened.basecase = number_screened.basecase_5,# - number_screened.basecase_0,
       prevalent_infections = prevalent_infections_5,
       prevalent_infections.basecase = prevalent_infections.basecase_5,
       incident_cases = incident_cases_5,# - incident_cases_0,
       incident_cases.basecase = incident_cases.basecase_5,# - incident_cases.basecase_0,
       population_size = population_size_5) 

  df5 <- df5 %>% 
    select(grep("^[a-z\\\\._]*$", colnames(df5), value=T))

  head(df5)

  df6 <- df5 %>% 
    mutate(
      prevalence = prevalent_infections / population_size,
      rr.incident_infections_averted = (incident_cases.basecase - incident_cases) / incident_cases.basecase,
      rr.additional_tests = (number_screened - number_screened.basecase)/(number_screened.basecase)) %>% 
  select(site, sim, interv, prevalence, rr.incident_infections_averted, rr.additional_tests)

  df6 <- df6 %>% 
    reshape2::melt(id.vars = c('site', 'sim', 'interv'))

  df7 <- df6 %>% 
    group_by(site, interv, variable) %>% 
    summarize(ci_high = quantile(value, 0.975, na.rm=T),
              median = median(value, na.rm=T),
              mean = mean(value, na.rm=T),
              ci_low = quantile(value, 0.025, na.rm=T))

  df8 <- df7 %>% 
    ungroup() %>% 
    setDT() %>% 
    data.table::dcast(site + interv ~ variable, value.var = c('ci_high', 'mean', 'median', 'ci_low'))

  percent <- function(x, digits = 2, format = "f", ...) {
    paste0(formatC(100 * x, format = format, digits = digits, ...), "%")
  }

  formatted_percents <- apply(df8[,3:ncol(df8)], 2, percent)

  orig_ncol <- ncol(df8)
  df8[,3:orig_ncol]  <- NULL
  df9 <- cbind.data.frame(df8, formatted_percents)

  .construct_interventions_description_df()

  df10 <- merge(df9, intervention_descriptions[, c('shortnames', 'names')], by.x = 'interv', by.y = 'shortnames')

  df11 <- as.data.frame(df10)[,c(2,ncol(df10),3:(ncol(df10)-1))]

  df11 %<>% arrange(site)

  write.csv(df11, file.path(
      system.file("intervention_analysis/", package='gcRegional'),
      'intervention_rr_prevalence_inf_averted_addt_tests.csv'))

  df12 <- df11 %>% 
    mutate(
      prevalence = paste0("Mean: ", mean_prevalence, 
                          " Median: ", median_prevalence,
                          " (", ci_low_prevalence, ", ", ci_high_prevalence, ")"),
      rr.incident_infections_averted = 
        paste0("Mean: ", mean_rr.incident_infections_averted, 
               " Median: ", median_rr.incident_infections_averted, 
               " (", ci_low_rr.incident_infections_averted, ", ", ci_high_rr.incident_infections_averted, ")"),
      rr.additional_tests = 
        paste0("Mean: ", mean_rr.additional_tests, 
               " Median: ", median_rr.additional_tests, 
               " (", ci_low_rr.additional_tests, ", ", ci_high_rr.additional_tests, ")")) %>% 
    select(c('site', 'names', 'prevalence', 'rr.incident_infections_averted', 'rr.additional_tests'))

  write.csv(df12, file.path(
      system.file("intervention_analysis/", package='gcRegional'),
      'intervention_rr_prevalence_inf_averted_addt_tests_formatted.csv'), row.names=FALSE)
}
# .render_intervention_summary_table()
```

### NNT Table

```{r}

# nt_ca_df <- readRDS(file.path(
#   system.file(
#     package = 'gcRegional',
#     "intervention_analysis/data/"
#   ),
#   'additional_tests_(pct)_cases_averted_(pct)_and_nnt3.rds'
# ))
# 
# used_interventions <- readRDS(system.file("intervention_analysis/used_interven
# tions.rds", package='gcRegional'))
# 
# main_interventions <- used_interventions[-grep("high_activity|ltfu", used_interventions)]
# 
# nt <- nt_ca_df %>% filter(variable == 'Number Needed to Test') %>% 
#   filter(interv %in% c(main_interventions, '1year_high_activity_semi_annual')) %>% 
#   select(site, names, mean, ci_high, ci_low) %>%
#   arrange(site)
# 
# formatter <- function(x, digits = 1, format = "f", ...) {
#   formatC(x, format = format, digits = digits, ...)
# }
# 
# formatted_data <- apply(nt[,3:5], 2, formatter)
# 
# nt[,3:5] <- formatted_data
# 
# nt$nnt <- paste0(nt$mean, " (", nt$ci_low, ", ", nt$ci_high, ")")
# 
# nt <- nt[, c('site', 'names', 'nnt')]
# 
# write.csv(nt, "~/Desktop/nnt.csv")
```


### Produce Outcomes table for Mobile outreach Sensitivity Scenarios

```{r}
# .render_intervention_summary_table_mobile_outreach <- function(site) { 
#   require(data.table)
# 
#   # df <- readRDS(system.file('intervention_analysis/interventions3.rds', package='gcRegional'))
#   mobile_ba <- readRDS(system.file('intervention_analysis/interventions_data_mobile_outreach_sensitivity_BA_fixed.rds', package='gcRegional'))
#   mobile_sf <- readRDS(system.file('intervention_analysis/interventions_data_mobile_outreach_sensitivity_SF_fixed.rds', package='gcRegional'))
# 
#   mobile_ba$site <- 'BA'
#   mobile_sf$site <- 'SF'
# 
#   df <- rbind.data.frame(mobile_ba, mobile_sf)
# 
# 
#   max_sf_year <- df %>% filter(site == 'SF') %>% `[[`('year') %>% max
#   max_ba_year <- df %>% filter(site == 'BA') %>% `[[`('year') %>% max
# 
#   df %<>% mutate(
#     year = ifelse(site == 'SF', year - max_sf_year + 5, year - max_ba_year + 5)) %>% 
#   filter(year %in% c(0,5))
# 
#   df %<>% filter(population == 'All') 
# 
#   df2 <- df %>% 
#     select(-population) %>% 
#     mutate(prevalent_infections = symptomatic_cases + asymptomatic_cases) %>% 
#     select(-c(symptomatic_cases, asymptomatic_cases)) %>% 
#     select(-diagnosed_cases)
# 
#   basecase_df <- df2 %>% filter(interv == 'base_case') %>% select(-interv)
# 
#   df3 <- merge(df2, basecase_df, by = c('site', 'sim', 'year'), suffixes = c('', '.basecase'))
# 
#   df4 <- data.table::dcast(setDT(df3), site + sim + interv ~ year,
#     value.var =  colnames(df3)[5:ncol(df3)])
# 
# 
#    df5 <- 
#      df4 %>% 
#      mutate(
#        number_screened = number_screened_5,# - number_screened_0,
#        number_screened.basecase = number_screened.basecase_5,# - number_screened.basecase_0,
#        prevalent_infections = prevalent_infections_5,
#        prevalent_infections.basecase = prevalent_infections.basecase_5,
#        incident_cases = incident_cases_5,# - incident_cases_0,
#        incident_cases.basecase = incident_cases.basecase_5,# - incident_cases.basecase_0,
#        population_size = population_size_5) 
# 
#   df5 <- df5 %>% 
#     select(grep("^[a-z\\\\._]*$", colnames(df5), value=T))
# 
#   head(df5)
# 
#   df6 <- df5 %>% 
#     mutate(
#       prevalence = prevalent_infections / population_size,
#       rr.incident_infections_averted = (incident_cases.basecase - incident_cases) / incident_cases.basecase,
#       rr.additional_tests = (number_screened - number_screened.basecase)/(number_screened.basecase)) %>% 
#   select(site, sim, interv, prevalence, rr.incident_infections_averted, rr.additional_tests)
# 
#   df6 <- df6 %>% 
#     reshape2::melt(id.vars = c('site', 'sim', 'interv'))
# 
#   saveRDS(df6, file.path(system.file("intervention_analysis/", package='gcRegional'),
#       'intervention_rr_prevalence_inf_averted_addt_tests_mobile_outreach.rds'))
# 
# 
#   df7 <- df6 %>% 
#     group_by(site, interv, variable) %>% 
#     summarize(ci_high = quantile(value, 0.975, na.rm=T),
#               median = median(value, na.rm=T),
#               mean = mean(value, na.rm=T),
#               ci_low = quantile(value, 0.025, na.rm=T))
# 
#   df8 <- df7 %>% 
#     ungroup() %>% 
#     setDT() %>% 
#     data.table::dcast(site + interv ~ variable, value.var = c('ci_high', 'mean', 'median', 'ci_low'))
# 
#   percent <- function(x, digits = 2, format = "f", ...) {
#     paste0(formatC(100 * x, format = format, digits = digits, ...), "%")
#   }
# 
#   formatted_percents <- apply(df8[,3:ncol(df8)], 2, percent)
# 
#   orig_ncol <- ncol(df8)
#   df8[,3:orig_ncol]  <- NULL
#   df9 <- cbind.data.frame(df8, formatted_percents)
# 
#   .construct_interventions_description_df()
# 
#   df10 <- merge(df9, intervention_descriptions[, c('shortnames', 'names')], by.x = 'interv', by.y = 'shortnames')
# 
#   df11 <- as.data.frame(df10)[,c(2,ncol(df10),3:(ncol(df10)-1))]
# 
#   df11 %<>% arrange(site)
# 
#   write.csv(df11, file.path(
#       system.file("intervention_analysis/", package='gcRegional'),
#       'intervention_rr_prevalence_inf_averted_addt_tests_mobile_outreach.csv'))
# 
#   df12 <- df11 %>% 
#     mutate(
#       prevalence = paste0("Mean: ", mean_prevalence, 
#                           " Median: ", median_prevalence,
#                           " (", ci_low_prevalence, ", ", ci_high_prevalence, ")"),
#       rr.incident_infections_averted = 
#         paste0("Mean: ", mean_rr.incident_infections_averted, 
#                " Median: ", median_rr.incident_infections_averted, 
#                " (", ci_low_rr.incident_infections_averted, ", ", ci_high_rr.incident_infections_averted, ")"),
#       rr.additional_tests = 
#         paste0("Mean: ", mean_rr.additional_tests, 
#                " Median: ", median_rr.additional_tests, 
#                " (", ci_low_rr.additional_tests, ", ", ci_high_rr.additional_tests, ")")) %>% 
#     select(c('site', 'names', 'prevalence', 'rr.incident_infections_averted', 'rr.additional_tests'))
# 
#   write.csv(df12, file.path(
#       system.file("intervention_analysis/", package='gcRegional'),
#       'intervention_rr_prevalence_inf_averted_addt_tests_formatted_mobile_outreach.csv'), row.names=FALSE)
# }
# .render_intervention_summary_table_mobile_outreach()
```

# Plot Additional Tests and Incident Infections Averted

```{r}
# 
#   make_additional_tests_and_cases_averted_mobile_outreach_plot <- function(
#     city = c("Baltimore", "San Francisco")[rbinom(1,1,.5)+1], 
#     interventions_list = hypothetical_interventions, 
#     subtitle = NULL, 
#     include_nnt = F) {
# 
#     require(rlang)
#     city <- rlang::enquo(city)
#     
#     df <- readRDS(file.path(system.file("intervention_analysis/", package='gcRegional'),
#       'intervention_rr_prevalence_inf_averted_addt_tests_mobile_outreach.rds'))
# 
#     df$variable %<>% recode(rr.additional_tests = 'Additional Tests (%)'
# 
# 
#     df <- dplyr::filter(nnt_df, 
#                   site == !! c(`Baltimore` = 'BA', `San Francisco`='SF')[[quo_name(city)]], 
#                   interv %in% interventions_list)
# 
#     # df <- reshape2::melt(df, id.vars = c('site', 'sim', 'interv'))
#     
#     ggplot(df, aes(x=names, y = value*100)) + 
#     geom_hline(data = data.frame(variable = c('Additional Tests (%)', 'Infections Averted (%)'), yintercept = c(NA, 0)), 
#                mapping = aes(yintercept=yintercept), color='red', alpha=0.5) + 
#     geom_jitter(
#     data = df %>% filter(
#       sim %in% sample.int(n=1000, size=250)),
#     mapping = aes(color = names), width = 0.25, alpha = 0.5) + 
#     geom_boxplot(
#       width = .5, 
#       outlier.shape = NA, 
#       alpha = 0.5
#       ) + 
#     ggtitle(paste0(c(`Baltimore` = 'A) ', `San Francisco` = 'B) ')[[rlang::quo_name(city)]], "Intervention Outcomes in ", rlang::quo_name(city))) + 
#     theme_bw() + 
#     facet_wrap(~variable, scales = 'free_x') + 
#     coord_flip()  +
#     xlab("") + 
#     expand_limits(y=0) + 
#     theme(axis.title.x = element_text(hjust = 1), legend.position = 'none', 
#           axis.text.x = element_text(hjust=.5),
#           panel.grid.major.y = element_blank(),
#           panel.grid.minor.y = element_blank(),
#           plot.margin = margin(10, 15, 10, 10)) + 
#     ylab("Additional Tests and Infections Averted as a Percentage of the Base Case") + 
#     scale_color_manual(values = setNames(
#       sapply(
#       intervention_descriptions$color, colorspace::lighten, .5),
#       intervention_descriptions$names
#     ))
#   }
```

