---
title: Status Report on gcRegional
---

In this report I'll outline a status update on the following aspects
of the project. 

- Model Structure
- Optimization
- Calibration
- Intervention Analysis

## Model Structure and Optimization

Because optimization has been difficult, we have been trying to make 
the posterior distribution easier to optimize. 

To this end, we have tried many things: 

- Fixing Parameters to Medians from the National Model
- Using Logistic Curves instead of Bezier Curves for screening
- Forcing screening to be only increasing
- Scaling the population denominators for case rates and NHANES data down
- Setting a more narrow prior on the reporting probability of symptomatic cases

What has been the most successful has been scaling the case rate and NHANES
population denominators down. The idea goes that the populations behind these numbers
are so large that the beta distributions used in the likelihood are too sharp, and thus
the model prioritizes hitting individual data points rather than interpolating the trend. 

Setting a more narrow prior for the probability of reporting symptomatic cases 
(with a 95% confidence interval [60% to 95%]) has been helpful for informing the 
reporting probabilities which usually vary across the entire range. However, 
several demographic groups have reporting probabilities which converge to 
values outside of this range, and these do not seem to be very strongly affected
by the change in the prior. I think this is OK, as it helps the otherwise uninformed 
parameters to find a satisfactory value for optimization while leaving the 
parameters which seem to be informed by the likelihood function mostly unchanged. 

Optimizing the model has been tricky; this is due to the many parameters which are 
rather uninformed in the model. These include the reporting symptomatic cases probabilities, 
the bezier curve control points, and the risk group mixing rates. 

We mention above how the symptomatic reporting probabilities have been altered to 
try and improve optimization. We have tried changing out the bezier curves for logistic curves,
and this results in optimization which converges in the units value in both settings. However
the model fit which optimizations converge to does not interpolate the case rates very well at all,
often with model case rates greater than the reported case rates across the whole data time-period.

We do not think that the risk mixing parameters should be informed by the national model's estimates.

Given this, we are currently continuing to optimize the model using the scaled down 
population denominators and fixing 12 natural history parameters to the national model's 
medians.

## Calibration

Calibration is dependent upon finding optimal values to start the model with. Nonetheless, 
we have calibrated the model from our best previous optimizations to get temporarily satisfactory
results. The acceptance rate is not great, but it is sufficient to get a sample of 1000 from the 
posterior if mcmc is run for long enough (2-4 days, 25 parallel chains). 

## Intervention Analysis


I'm interested in investigating the following questions: 


What has the effect of screening in the data period been? 

  - How has screening affected different risk groups? 
  
  - How many cases have been averted? 
  
  - What has the relative reduction in prevalence been? 

  
  
How is the burden of disease distributed? 

  - What is the prevalence rate ratio across demographics and sex 
  in the last data year?
  
  - What is the incidence rate ratio across demographics and sex 
  in the last data year? 
  
  - What is the distribution of incident cases during the entire
  data period across demographics and sex? 

 

How do the following interventions compare

  - Improvements to Current Interventions
  
  - Interventions Targeted on the Elevated Burden Populations
  
  - Demographically Targeted Interventions
  
  - Universal Screening
  
  * In specific, how do they compare in the following metrics: 
  
    - Cases Averted
    
    - Number of Additional Tests
    
    - Relative Reduction in Prevalence
    
    - Number Needed to Screen to Avert One Additional Case
    
    - Number Needed to Screen to Avert One Case
  



We will the following information, in figures and data. 

- Incidence (still needed) and Prevalence (✔)︎, broken into Men and Women, and each Demographic Group

- Relative Rate of Prevalence(✔︎)/Incidence compared to Population Rate for each Demographic Group

- Cases Averted in the Data Period due to Screening (retrospective) (still needed)
  - The effect of screening in the data period on men, women, and each demographic group.

- Cases Averted, Number of Additional Tests, and Number Needed to Screen to Avert One Case
  - We will analyze several interventions, focused on removing LTFU, 
    and increasing screening in those populations with a rate of incidence greater
    than the population average.
  - We could also implement the US guidelines... Then we'd have "baseline", and "enhanced,"
    and we could pretty easily do universal coverage as well. (still needed)

```{r get interventions data, cache = T}
sf_df <- readRDS("~/Documents/gcRegional/output/10-22-18/interventions_data_SF.rds")
ba_df <- readRDS("~/Documents/gcRegional/output/10-22-18/interventions_data_BA.rds")
```

### Prevalence Plots

```{r calculating all population prevalence, cache=T}
df <- do.call(
  rbind, 
  list(
    cbind.data.frame(site = 'BA', filter(
      ba_df,
      variable %in% c('population_size', 'asymptomatic_cases', 'symptomatic_cases'),
      population %in% c('Male', 'Female'),
      interv == 'base_case'
      )),
      cbind.data.frame(site = 'SF', filter(
      sf_df,
      variable %in% c('population_size', 'asymptomatic_cases', 'symptomatic_cases'),
      population %in% c('Male', 'Female'),
      interv == 'base_case'
      ))
      ))

df <- reshape2::dcast(df, site + sim + year ~ variable + population, value.var = 'value')

summary_df <- group_by(df, site, sim, year) %>% 
  summarize(
    prevalence = (
    symptomatic_cases_Male + symptomatic_cases_Female + 
      asymptomatic_cases_Male + asymptomatic_cases_Female
    ) / (population_size_Male + population_size_Female)
    )

ci_df <- group_by(summary_df, site, year) %>% 
  summarise(mean = mean(prevalence, na.rm=T),
            ci_high = quantile(prevalence, 0.975, na.rm = T),
            ci_low = quantile(prevalence, 0.025, na.rm = T))

library(ggplot2)

# ci_df$interv <- sapply(ci_df$interv, function(str) paste0(strwrap(gsub("_", " ", str), width = 15), collapse='\n'))

ggplot(ci_df, aes(x = year, y = mean, ymax = ci_high, ymin = ci_low)) + 
  geom_ribbon(size = 0, alpha=0.5) + 
  geom_line() + 
  facet_wrap(~site) + 
  theme_bw() + 
  theme(legend.position = 'none') + 
  scale_x_continuous(breaks = seq(min(ci_df$year), max(ci_df$year), by = 4)) + 
  ylab("Prevalence") + 
  ggtitle("Prevalence Estimates by Site")

# ggsave("~/Documents/gcRegional/output/10-29-18/intervention_analysis_plots/prevalence_all_pop.png", height = unit(4, 'in'))

```

```{r calculating prevalence by male/female}
df <- do.call(
  rbind, 
  list(
    cbind.data.frame(site = 'BA', filter(
      ba_df,
      variable %in% c('population_size', 'asymptomatic_cases', 'symptomatic_cases'),
      population %in% c('Male', 'Female'),
      interv == 'base_case'
      )),
      cbind.data.frame(site = 'SF', filter(
      sf_df,
      variable %in% c('population_size', 'asymptomatic_cases', 'symptomatic_cases'),
      population %in% c('Male', 'Female'),
      interv == 'base_case'
      ))
      ))

df <- reshape2::dcast(df, site + sim + year + population ~ variable, value.var = 'value')

summary_df <- group_by(df, site, sim, population, year) %>% 
  summarize(
    prevalence = (symptomatic_cases + asymptomatic_cases) / population_size
    )

ci_df <- group_by(summary_df, site, population, year) %>% 
  summarise(
    mean = mean(prevalence, na.rm=T),
    ci_high = quantile(prevalence, 0.975, na.rm = T),
    ci_low = quantile(prevalence, 0.025, na.rm = T)
    )

ggplot(ci_df, aes(x = year, y = mean, ymax = ci_high, ymin = ci_low, fill = population)) + 
  geom_ribbon(size = 0, alpha=0.5) + 
  geom_line(alpha=0.25) + 
  facet_grid(population~site) + 
  theme_bw() + 
  theme(legend.position = 'none') + 
  scale_x_continuous(breaks = seq(min(ci_df$year), max(ci_df$year), by = 4)) + 
  ylab("Prevalence") + 
  ggtitle("Prevalence Estimates by Site by Sex")

# ggsave("~/Documents/gcRegional/output/10-29-18/intervention_analysis_plots/prevalence_sex.png", height = unit(4, 'in'))
```

```{r calculating prevalence by demographic}
df <- do.call(
  rbind, 
  list(
    cbind.data.frame(site = 'BA', filter(
      ba_df,
      variable %in% c('population_size', 'asymptomatic_cases', 'symptomatic_cases'),
      population %in% c('Black', 'Other', 'Hispanic', 'MSM'),
      interv == 'base_case'
      )),
      cbind.data.frame(site = 'SF', filter(
      sf_df,
      variable %in% c('population_size', 'asymptomatic_cases', 'symptomatic_cases'),
      population %in% c('Black', 'Other', 'Hispanic', 'MSM'),
      interv == 'base_case'
      ))
      ))

df <- reshape2::dcast(df, site + sim + year + population ~ variable, value.var = 'value')

summary_df <- group_by(df, site, sim, population, year) %>% 
  summarize(
    prevalence = (symptomatic_cases + asymptomatic_cases) / population_size
    )

ci_df <- group_by(summary_df, site, population, year) %>% 
  summarise(
    mean = mean(prevalence, na.rm=T),
    ci_high = quantile(prevalence, 0.975, na.rm = T),
    ci_low = quantile(prevalence, 0.025, na.rm = T)
    )

ggplot(ci_df, aes(x = year, y = mean, ymax = ci_high, ymin = ci_low, fill = population)) + 
  geom_ribbon(size = 0, alpha=0.5) + 
  geom_line(alpha=0.25) + 
  facet_grid(population~site) + 
  theme_bw() + 
  theme(legend.position = 'none') + 
  scale_x_continuous(breaks = seq(min(ci_df$year), max(ci_df$year), by = 4)) + 
  ylab("Prevalence") + 
  ggtitle("Prevalence Estimates by Site by Demographic")

# ggsave("~/Documents/gcRegional/output/10-29-18/intervention_analysis_plots/prevalence_demographic.png", height = unit(4, 'in'))

```

### Prevalence Rate Ratios

```{r prevalence rate ratios}
df <- do.call(
  rbind, 
  list(
    cbind.data.frame(site = 'BA', filter(
      ba_df,
      variable %in% c('population_size', 'asymptomatic_cases', 'symptomatic_cases'),
      population %in% c('Male', 'Female'),
      interv == 'base_case'
      )),
      cbind.data.frame(site = 'SF', filter(
      sf_df,
      variable %in% c('population_size', 'asymptomatic_cases', 'symptomatic_cases'),
      population %in% c('Male', 'Female'),
      interv == 'base_case'
      ))
      ))

df <- reshape2::dcast(df, site + sim + year ~ variable + population, value.var = 'value')

all_pop_summary_df <- group_by(df, site, sim, year) %>% 
  summarize(
    prevalence = (
    symptomatic_cases_Male + symptomatic_cases_Female + 
      asymptomatic_cases_Male + asymptomatic_cases_Female
    ) / (population_size_Male + population_size_Female)
    )

# per population
df <- do.call(
  rbind, 
  list(
    cbind.data.frame(site = 'BA', filter(
      ba_df,
      variable %in% c('population_size', 'asymptomatic_cases', 'symptomatic_cases'),
      population %in% c('Black Male', 'Black Female', 'Other Male', 'Other Female', 'Hispanic Male', 'Hispanic Female', 'MSM'),
      interv == 'base_case'
      )),
      cbind.data.frame(site = 'SF', filter(
      sf_df,
      variable %in% c('population_size', 'asymptomatic_cases', 'symptomatic_cases'),
      population %in% c('Black Male', 'Black Female', 'Other Male', 'Other Female', 'Hispanic Male', 'Hispanic Female', 'MSM'),
      interv == 'base_case'
      ))
      ))

df <- reshape2::dcast(df, site + sim + year + population ~ variable, value.var = 'value')

summary_df <- group_by(df, site, sim, population, year) %>% 
  summarize(
    prevalence = (symptomatic_cases + asymptomatic_cases) / population_size
    )

summary_df <- merge(summary_df, all_pop_summary_df, by = c('site', 'sim', 'year'))

colnames(summary_df)[c(5,6)] <- c('demographic_prevalence', 'all_pop_prevalence')

summary_df <- mutate(summary_df, 
                     RR = demographic_prevalence / all_pop_prevalence)

ci_df <- group_by(summary_df, site, population, year) %>% 
  summarise(
    mean = mean(RR, na.rm = T),
    ci_high = quantile(RR, 0.975, na.rm = T),
    ci_low = quantile(RR, 0.025, na.rm = T),
    iq_high = quantile(RR, 0.75, na.rm = T),
    iq_low = quantile(RR, 0.25, na.rm = T)
  )

ci_df <- filter(ci_df, site == 'BA' & year == 2017 | site == 'SF' & year == 2016)
    
ci_df$site <- sapply(ci_df$site, function(x) c(SF = 'San Francisco', BA = 'Baltimore')[[x]])

ggplot(ci_df, aes(x = population, middle = mean, ymax = ci_high, ymin = ci_low, upper = iq_high, lower = iq_low, fill = population)) + 
  geom_boxplot(stat = 'identity') + 
  facet_grid(~site) + 
  geom_hline(aes(group = 1), yintercept = 1, linetype = 'dashed', color = 'red') + 
  theme_bw() + 
  theme(legend.position = 'none', axis.text.x = element_text(angle = 25, vjust = .5)) + 
  ylab("Prevalence Relative Rate") + 
  xlab("Demographic Groups")  + 
  ggtitle("Relative Rates of Prevalence")

ggsave("~/Documents/gcRegional/output/10-29-18/intervention_analysis_plots/prevalence_rate_ratio.png", height = unit(4, 'in'))

```



```{r incidence rate ratios}
df <- do.call(
  rbind, 
  list(
    cbind.data.frame(site = 'BA', filter(
      ba_df,
      variable %in% c('population_size', 'incident_cases'),
      population %in% c('Male', 'Female'),
      interv == 'base_case',
      year %in% c(2021, 2022)
      )),
      cbind.data.frame(site = 'SF', filter(
      sf_df,
      variable %in% c('population_size', 'incident_cases'),
      population %in% c('Male', 'Female'),
      interv == 'base_case',
      year %in% c(2020, 2021)
      ))
      ))

df <- reshape2::dcast(df, site + sim + year ~ variable + population, value.var = 'value')

df <- mutate(df, incidents = incident_cases_Male + incident_cases_Female,
             popsize = population_size_Male + population_size_Female) %>% 
  select(-c(incident_cases_Male, incident_cases_Female, population_size_Male, population_size_Female))

popsize_sf <- 303441.2
popsize_ba <- 207800.2

df <- do.call(rbind.data.frame, list(
  filter(df, site == 'SF') %>% select(-popsize) %>% 
    dcast(site + sim ~ year) %>% mutate(incidents = (`2021` - `2020`)/popsize_sf) %>%
    select(site, sim, incidents),
  filter(df, site == 'BA') %>% select(-popsize) %>% 
    dcast(site + sim ~ year) %>% mutate(incidents = (`2022` - `2021`)/popsize_ba) %>%
    select(site, sim, incidents)
))

incidence_in_last_year <- df



# Now per population

df <- do.call(
  rbind, 
  list(
    cbind.data.frame(site = 'BA', filter(
      ba_df,
      variable %in% c('population_size', 'incident_cases'),
      population %in% c('Black Male', 'Black Female', 'Other Male', 'Other Female', 'Hispanic Male', 'Hispanic Female', 'MSM'),
      interv == 'base_case',
      year %in% c(2021, 2022)
      )),
      cbind.data.frame(site = 'SF', filter(
      sf_df,
      variable %in% c('population_size', 'incident_cases'),
      population %in% c('Black Male', 'Black Female', 'Other Male', 'Other Female', 'Hispanic Male', 'Hispanic Female', 'MSM'),
      interv == 'base_case',
      year %in% c(2020, 2021)
      ))
      ))

# df <- do.call(rbind.data.frame, list(
#   filter(df, site == 'SF') %>% 
#     dcast(site + sim ~ year, value.var = c(incident_cases, pop
# ))

library(data.table)
df <- reshape2::dcast(df, site + sim + year + population ~ variable, value.var = 'value')

df <- do.call(rbind.data.frame, list(
  dcast(data.table::setDT(filter(df, site == 'SF')), site + sim + population ~ year, value.var = c('incident_cases', 'population_size')) %>% 
    mutate(incidence = (incident_cases_2021 - incident_cases_2020) / population_size_2021) %>% 
    select(-c(incident_cases_2021, incident_cases_2020, population_size_2021, population_size_2020)),
  
  dcast(data.table::setDT(filter(df, site == 'BA')), site + sim + population ~ year, value.var = c('incident_cases', 'population_size')) %>% 
    mutate(incidence = (incident_cases_2022 - incident_cases_2021) / population_size_2021) %>% 
    select(-c(incident_cases_2021, incident_cases_2022, population_size_2021, population_size_2022))
))

colnames(incidence_in_last_year)[3] <- 'all_pop_incidence'
df <- merge(df, incidence_in_last_year, by = c('site', 'sim'))
df <- mutate(df, incidence_rr = incidence / all_pop_incidence)

summary_df <- group_by(df, site, population) %>% 
  summarize(
    ci_high = quantile(incidence_rr, 0.975,  na.rm = T),
    iq_high = quantile(incidence_rr, 0.75,  na.rm = T),
    mean = mean(incidence_rr, na.rm = T),
    iq_low = quantile(incidence_rr, 0.25,  na.rm = T),
    ci_low = quantile(incidence_rr, 0.025,  na.rm = T))

summary_df$site <- sapply(summary_df$site, function(x) c(SF = 'San Francisco', BA = 'Baltimore')[[x]])

ggplot(summary_df, aes(x = population, middle = mean, ymax = ci_high, ymin = ci_low, upper = iq_high, lower = iq_low, fill = population)) + 
  geom_boxplot(stat = 'identity') + 
  facet_grid(~site) + 
  geom_hline(aes(group = 1), yintercept = 1, linetype = 'dashed', color = 'red') + 
  theme_bw() + 
  theme(legend.position = 'none', axis.text.x = element_text(angle = 25, vjust = .5)) + 
  ylab("Incidence Relative Rate") + 
  xlab("Demographic Groups") + 
  ggtitle("Relative Rates of Incidence")

ggsave("~/Documents/gcRegional/Rmd/2018/CDC Update Nov 6/incidence_rate_ratio.png", height = unit(4, 'in'))

```


```{r distribution of burden}
df <- do.call(
  rbind, 
  list(
    cbind.data.frame(site = 'BA', filter(
      ba_df,
      variable %in% c('population_size', 'incident_cases'),
      population %in% c('Black Male', 'Black Female', 'Other Male', 'Other Female', 'Hispanic Male', 'Hispanic Female', 'MSM'),
      interv == 'base_case',
      year %in% c(2021, 2022)
      )),
      cbind.data.frame(site = 'SF', filter(
      sf_df,
      variable %in% c('population_size', 'incident_cases'),
      population %in% c('Black Male', 'Black Female', 'Other Male', 'Other Female', 'Hispanic Male', 'Hispanic Female', 'MSM'),
      interv == 'base_case',
      year %in% c(2020, 2021)
      ))
      ))

library(data.table)
df <- reshape2::dcast(df, site + sim + year + population ~ variable, value.var = 'value')

df <- do.call(rbind.data.frame, list(
  dcast(filter(df, site == 'SF') %>% select(-population_size), site + sim + population ~ year) %>% 
    mutate(incidents = (`2021` - `2020`)) %>% 
    select(-c(`2021`, `2020`)),
  
  dcast(filter(df, site == 'BA'), site + sim + population ~ year, value.var = 'incident_cases') %>% 
    mutate(incidents = (`2022` - `2021`)) %>% 
    select(-c(`2021`, `2022`))
))

summary_df <- group_by(df, site, population) %>% 
  summarize(
    ci_high = quantile(incidents, 0.975,  na.rm = T),
    iq_high = quantile(incidents, 0.75,  na.rm = T),
    mean = mean(incidents, na.rm = T),
    iq_low = quantile(incidents, 0.25,  na.rm = T),
    ci_low = quantile(incidents, 0.025,  na.rm = T))

# SF_total_cases <- filter(summary_df, site == 'SF')['mean']
# BA_total_cases <- filter(summary_df, site == 'BA')['mean']

summary_df_normalized <- group_by(df, site, sim) %>% 
  mutate(fraction_of_all_incidents = incidents / sum(incidents))

summary_df_normalized2 <- group_by(summary_df_normalized, site, population) %>% 
  summarize(
    ci_high = quantile(fraction_of_all_incidents, 0.975,  na.rm = T),
    iq_high = quantile(fraction_of_all_incidents, 0.75,  na.rm = T),
    mean = mean(fraction_of_all_incidents, na.rm = T),
    iq_low = quantile(fraction_of_all_incidents, 0.25,  na.rm = T),
    ci_low = quantile(fraction_of_all_incidents, 0.025,  na.rm = T))

# summary_df_normalized <- 
#   group_by(summary_df, site) %>% 
#     mutate_if(is.numeric, funs(norm = . / sum(.)))


ggplot(summary_df_normalized2, aes(x = population, y = mean, fill = population, color = population)) + 
  geom_bar(stat = 'identity') + 
  facet_wrap(~site) + 
  ylab("Fraction of Incident Cases Among Demographic") + 
  xlab("Demographic Groups") + 
  theme(axis.text.x = element_text(angle = 25, vjust = 0.5)) 
```

```{r}

summary_df_normalized2$site <- sapply(as.character(summary_df_normalized2$site), function(x) c(BA = 'Baltimore', SF = 'San Francisco')[[x]])
ggplot(
  summary_df_normalized2,
  aes(
  x = population,
  y = 100*mean,
  ymax = 100*ci_high,
  ymin = 100*ci_low,
  lower = 100*iq_low,
  upper = 100*iq_high,
  fill = population
  )
  ) + 
  # geom_boxplot(stat = 'identity') + 
  geom_bar(stat = 'identity') + 
  geom_errorbar(stat = 'identity', width = 0.2, alpha=0.5) + 
  facet_wrap(~site) + 
  ylab("Percentage of Cases in Demographic") + 
  xlab("Demographic Groups") + 
  ggtitle("Percentage of Cases in Each Demographic") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 25, vjust = 0.5), legend.position = 'none') 

ggsave("~/Documents/gcRegional/Rmd/2018/CDC Update Nov 6/distribution_of_cases.png", height = unit(5, 'in'))
```

```{r}
ggplot(summary_df, aes(x = population, y = mean, fill = population, color = population)) + 
  geom_bar(stat = 'identity') + 
  facet_wrap(~site) + 
  ylab("Incident Cases Among Demographic") + 
  xlab("Demographic Groups") + 
  theme(axis.text.x = element_text(angle = 25, vjust = 0.5)) 

```


### Intervention Analysis Results

```{r get pre-computed intervention analysis results, cache = T}
intervention_results <- readRDS(file.path(system.file("intervention_simulations", package = 'gcRegional'), 'intervention_results.rds'))
intervention_results <- intervention_results[complete.cases(intervention_results), ]

intervention_results <- mutate(intervention_results, nns = additional_tests / cases_averted)

ir_summary <- group_by(intervention_results, site, interv) %>% 
  summarize(
    ci_high_cases_averted = quantile(cases_averted, .975),
    iq_high_cases_averted = quantile(cases_averted, .75),
    median_cases_averted = median(cases_averted),
    iq_low_cases_averted = quantile(cases_averted, .25),
    ci_low_cases_averted = quantile(cases_averted, .025),
    ci_high_nns = quantile(nns, 0.975),
    iq_high_nns = quantile(nns, 0.75),
    median_nns = median(nns),
    iq_low_nns = quantile(nns, 0.25),
    ci_low_nns = quantile(nns, 0.025),
    ci_high_tests = quantile(additional_tests, 0.975),
    iq_high_tests = quantile(additional_tests, 0.75),
    median_tests = median(additional_tests),
    iq_low_tests = quantile(additional_tests, 0.25),
    ci_low_tests = quantile(additional_tests, 0.025)
  )

intervention_results$site <- ifelse(intervention_results$site == 'SF', 'San Francisco', 'Baltimore')
ir_summary$site <- ifelse(ir_summary$site == 'SF', 'San Francisco', 'Baltimore')
ir_summary$interv <- ordered(ir_summary$interv, levels = rev(intervention_descriptions$shortnames))

  intervention_descriptions <- do.call(
    cbind.data.frame,
    list(
      shortnames = 
        c(
          "base_case",
          "high_activity_young_annual",
          "high_activity_young_semi_annual",
          "high_activity_young_quarter_annual",
          "young_annual",
          "young_semi_annual",
          "young_quarter_annual",
          "high_activity_MSM_annual",
          "high_activity_MSM_semi_annual",
          "high_activity_MSM_quarter_annual",
          "MSM_annual",
          "MSM_semi_annual",
          "MSM_quarter_annual",
          "high_activity_annual",
          "high_activity_semi_annual",
          "high_activity_quarter_annual",
          "female_young_annual",
          "female_young_semi_annual",
          "female_young_quarter_annual",
          "remove_ltfu_10pct",
          "remove_ltfu_20pct",
          "remove_f_msm_10pct_and_msw_20pct_ltfu",
          "1year_high_activity_semi_annual"
          ), 
      names =
        c(
        base_case = "Base Case",
        high_activity_young_annual = "High Risk Young Annual Screening",
        high_activity_young_semi_annual = "High Risk Young Semi-Annual Screening",
        high_activity_young_quarter_annual = "High Risk Young Quarter-Annual Screening",
        young_annual = "Young Annual Screening",
        young_semi_annual = "Young Semi-Annual Screening",
        young_quarter_annual = "Young Quarter-Annual Screening",
        high_activity_MSM_annual = "High Risk MSM Annual Screening",
        high_activity_MSM_semi_annual = "High Risk MSM Semi-Annual Screening",
        high_activity_MSM_quarter_annual = "High Risk MSM Quarter-Annual Screening",
        MSM_annual = "MSM Annual Screening",
        MSM_semi_annual = "MSM Semi-Annual Screening",
        MSM_quarter_annual = "MSM Quarter-Annual Screening",
        high_activity_annual = "High Risk Annual Screening",
        high_activity_semi_annual = "High Risk Semi-Annual Screening",
        high_activity_quarter_annual = "High Risk Quarter Annual Screening",
        female_young_annual = "Female Young Annual Screening",
        female_young_semi_annual = "Female Young Semi-Annual Screening",
        female_young_quarter_annual = "Female Young Quarter-Annual Screening",
        remove_ltfu_10pct = "Remove 10% LTFU",
        remove_ltfu_20pct = "Remove 20% LTFU",
        remove_f_msm_10pct_and_msw_20pct_ltfu = "Remove 10% LTFU for Women and MSM, 20% LTFU for MSW",
        `1year_high_activity_semi_annual` = 'High Activity Twice Annual Screening for One Year'
        ),
      frequency = 
        c(
          "base_case",
          "annual",
          "semi_annual",
          "quarter_annual",
          "annual",
          "semi_annual",
          "quarter_annual",
          "annual",
          "semi_annual",
          "quarter_annual",
          "annual",
          "semi_annual",
          "quarter_annual",
          "annual",
          "semi_annual",
          "quarter_annual",
          "annual",
          "semi_annual",
          "quarter_annual",
          "ltfu",
          "ltfu",
          "ltfu",
          "semi_annual"
          )
    )
  )
empirical_interventions <- c('remove_ltfu_10pct', 'remove_ltfu_20pct', 'remove_f_msm_10pct_and_msw_20pct_ltfu', '1year_high_activity_semi_annual')
interventions <- setdiff(unique(ba_df$interv), 'base_case')
```

```{r prevalence for interventions}

df <- do.call(
  rbind, 
  list(
    cbind.data.frame(site = 'BA', filter(ba_df, variable %in% c('population_size', 'asymptomatic_cases', 'symptomatic_cases'), population %in% c('Male', 'Female'))),
    cbind.data.frame(site = 'SF', filter(sf_df, variable %in% c('population_size', 'asymptomatic_cases', 'symptomatic_cases'), population %in% c('Male', 'Female')))
  ))

df <- reshape2::dcast(df, site + sim + interv + year ~ variable + population)

summary_df <- group_by(df, site, sim, interv, year) %>% 
  summarize(
    prevalence = (
    symptomatic_cases_Male + symptomatic_cases_Female + 
      asymptomatic_cases_Male + asymptomatic_cases_Female
    ) / (population_size_Male + population_size_Female)
    )

# incomplete_sims <- unique(summary_df[!complete.cases(summary_df), 'sim'])
# summary_df <- filter(summary_df, ! sim %in% incomplete_sims)

ci_df <- group_by(summary_df, site, interv, year) %>% 
  summarise(mean = mean(prevalence, na.rm=T),
            ci_high = quantile(prevalence, 0.975, na.rm = T),
            ci_low = quantile(prevalence, 0.025, na.rm = T))

for (year in 2010:2017) {
  ci_df[ci_df$year == year & ci_df$interv != 'base_case' & ci_df$site == 'BA', 'mean'] <- ci_df[ci_df$year == year & ci_df$interv == 'base_case' & ci_df$site == 'BA', 'mean']
}
for (year in 2010:2016) {
  ci_df[ci_df$year == year & ci_df$interv != 'base_case' & ci_df$site == 'SF', 'mean'] <- ci_df[ci_df$year == year & ci_df$interv == 'base_case' & ci_df$site == 'SF', 'mean']
}

library(ggplot2)

# # plotting each interventions prevalence in a facet

# ci_df$interv <- sapply(ci_df$interv, function(str) paste0(strwrap(gsub("_", " ", str), width = 15), collapse='\n'))
# 
# ggplot(ci_df, aes(x = year, y = mean, ymax = ci_high, ymin = ci_low, fill = interv, color = interv)) + 
#   geom_ribbon(size = 0, alpha=0.5) + 
#   geom_line() + 
#   facet_grid(site ~ interv) + 
#   theme(legend.position = 'none', axis.text.x = element_text(angle = 90)) + 
#   scale_x_continuous(breaks = seq(min(ci_df$year), max(ci_df$year), by = 4))


summary_df_dcast <- dcast(summary_df, site + sim + year ~ interv)

library(magrittr)



for (interv in interventions) {
    summary_df_dcast[[interv]] = summary_df_dcast[[interv]] / summary_df_dcast[['base_case']]
}

summary_df_dcast %<>% select(-base_case)

relative_summary_df <- melt(summary_df_dcast, id.vars = c('site', 'sim', 'year'), variable.name = 'interv', value.name = 'prevalence')

relative_ci_df <- relative_summary_df %>%  
  group_by(site, interv, year) %>% 
  summarise(mean = mean(prevalence, na.rm = T), 
            ci_high = quantile(prevalence, 0.975, na.rm = T),
            iq_high = quantile(prevalence, 0.75, na.rm = T),
            ci_low = quantile(prevalence, 0.025, na.rm = T),
            iq_low = quantile(prevalence, 0.25, na.rm = T))
  
library(ggrepel)

last_data_points_relative <- as.data.frame(do.call(
  rbind.data.frame,
  list(
    filter(relative_ci_df, site == 'BA', year == 2022),
    filter(relative_ci_df, site == 'SF', year == 2021)
  )))

last_data_points_absolute <- as.data.frame(do.call(
  rbind.data.frame,
  list(
    filter(ci_df, site == 'BA', year == 2022),
    filter(ci_df, site == 'SF', year == 2021)
  )))

library(ggrepel)

# Plot Mean Prevalence Time Trends


ci_df$site <-
  sapply(as.character(ci_df$site), function(x)
  c(SF = 'San Francisco', BA = 'Baltimore')[[x]])

last_data_points_absolute$site <-
  sapply(as.character(last_data_points_absolute$site), function(x)
  c(SF = 'San Francisco', BA = 'Baltimore')[[x]])

last_data_points_relative$site <-
  sapply(as.character(last_data_points_relative$site), function(x)
  c(SF = 'San Francisco', BA = 'Baltimore')[[x]])


ci_df[ci_df$site == 'San Francisco', 'year'] <- ci_df[ci_df$site == 'San Francisco', 'year'] - 2016
ci_df[ci_df$site == 'Baltimore', 'year'] <- ci_df[ci_df$site == 'Baltimore', 'year'] - 2017

last_data_points_absolute[last_data_points_absolute$site == 'San Francisco', 'year'] <-
  last_data_points_absolute[last_data_points_absolute$site == 'San Francisco', 'year'] - 2016
  last_data_points_absolute[last_data_points_absolute$site == 'Baltimore', 'year'] <-
  last_data_points_absolute[last_data_points_absolute$site == 'Baltimore', 'year'] - 2017
  
last_data_points_absolute <- merge(last_data_points_absolute, intervention_descriptions, by.x = 'interv', by.y = 'shortnames', all.x = T)
last_data_points_absolute$names <- ordered(last_data_points_absolute$names, levels = rev(intervention_descriptions$names))

  

ggplot(filter(ci_df, year >= 0, interv %in% c(empirical_interventions, 'base_case')), aes(x = year, y = 100*mean, color = interv)) + 
  geom_line() + 
  facet_wrap(~site) + 
  scale_x_continuous(
    breaks = seq(min(ci_df$year), max(ci_df$year), by = 1), 
    limits = c(0, 7)) +
  geom_label_repel(
    data = filter(last_data_points_absolute, interv %in% c(empirical_interventions, 'base_case')),
    aes(
    x = year,
    y = 100*mean,
    group = interv,
    label = interv
    ),
    segment.color = 'black',
    segment.size = 0.5,
    segment.alpha = 0.5,
    linetype = 'dashed',
    nudge_x = 2.5,
    direction = 'y',
    size = 2
    ) +
  expand_limits(y = 0) + 
  ylab("Prevalence") +
  xlab("Years After Intervention Start") + 
  theme_bw() + 
  theme(legend.position = 'none')

ggsave("~/Documents/gcRegional/output/10-29-18/intervention_analysis_plots/intervention_prevalence_absolute_empirical.png",   dpi = 300,
  width = unit(9, 'in'),
  height = unit(5, 'in')
  )


ggplot(filter(ci_df, year >= 0, ! interv %in% empirical_interventions), aes(x = year, y = 100*mean, color = interv)) + 
  geom_line() + 
  facet_wrap(~site) + 
  scale_x_continuous(
    breaks = seq(min(ci_df$year), max(ci_df$year), by = 1), 
    limits = c(0, 7)) +
  geom_label_repel(
    data = filter(last_data_points_absolute, ! interv %in% empirical_interventions ),
    aes(
    x = year,
    y = 100*mean,
    group = interv,
    label = interv
    ),
    segment.color = 'black',
    segment.size = .5,
    segment.alpha = 0.5,
    nudge_x = 2.5,
    direction = 'y',
    size = 2
    ) +
  ylab("Prevalence") +
  xlab("Years After Intervention Start") + 
  expand_limits(y=0) + 
  theme_bw() + 
  theme(legend.position = 'none')

ggsave("~/Documents/gcRegional/output/10-29-18/intervention_analysis_plots/intervention_prevalence_absolute_hypothetical.png",   dpi = 300,
  width = unit(9, 'in'),
  height = unit(5, 'in')
  )

last_data_points_relative <- merge(last_data_points_relative, intervention_descriptions, by.x = 'interv', by.y = 'shortnames', all.x = T)
last_data_points_relative$names <- ordered(last_data_points_relative$names, levels = rev(intervention_descriptions$names))

ggplot(
  filter(last_data_points_relative, interv %in% empirical_interventions),
  aes(
  x = names,
  middle = 100-100*mean,
  ymax = 100-100*ci_high,
  ymin = 100-100*ci_low,
  upper = 100-100*iq_high,
  lower = 100-100*iq_low
  ),
  alpha = 0.5
  ) + 
  geom_boxplot(stat = 'identity') + 
  facet_wrap(~site) + 
  coord_flip() + 
  theme_bw() + 
  theme(legend.position = 'none', axis.title.x = element_text(hjust = 1)) + 
  xlab("") + 
  ylab("Prevalence Reduction as a Percentage of Base Case Prevalence") + 
  expand_limits(y=0) + 
  ggtitle("Relative Reduction in Prevalence", subtitle = "Interventions Based on Current Strategies")

ggsave("~/Documents/gcRegional/output/10-29-18/intervention_analysis_plots/prevalence_ratio_in_last_year_empirical.png", height = unit(5, 'in'), width = unit(9, 'in'))

ggplot(
  filter(last_data_points_relative, ! interv %in% empirical_interventions),
  aes(
  x = names,
  middle = 100-100*mean,
  ymax = 100-100*ci_high,
  ymin = 100-100*ci_low,
  upper = 100-100*iq_high,
  lower = 100-100*iq_low
  ),
  alpha = 0.5
  ) + 
  geom_boxplot(stat = 'identity') + 
  facet_wrap(~site) + 
  coord_flip() + 
  theme_bw() + 
  theme(legend.position = 'none', axis.title.x = element_text(hjust = 1)) + 
  xlab("") + 
  ylab("Prevalence Reduction as a Percentage of Base Case Prevalence") + 
  expand_limits(y=0) + 
  ggtitle("Relative Reduction in Prevalence", subtitle = "Hypothetical Interventions")

ggsave("~/Documents/gcRegional/output/10-29-18/intervention_analysis_plots/prevalence_ratio_in_last_year_hypothetical.png", height = unit(5, 'in'), width = unit(9, 'in'))


```


```{r cases averted, cache = T}

ggplot(ir_summary) + 
  geom_boxplot(stat = 'identity', aes(x = interv, ymax = ci_high_cases_averted, upper = iq_high_cases_averted, middle = median_cases_averted, lower = iq_low_cases_averted, ymin = ci_low_cases_averted)) + 
  ggtitle("Number of Cases Averted After 5 Years by Intervention") + 
  geom_hline(yintercept = 0, linetype ='dashed', color = 'red', alpha = 0.5) +
  facet_wrap(~site) + 
  coord_flip()  
```


```{r intervention outcomes - additional tests and cases averted}
colnames(ir_summary) <- 
  c(
    'site',
    'interv',
    'ci_high cases_averted',
    'iq_high cases_averted',
    'median cases_averted',
    'iq_low cases_averted',
    'ci_low cases_averted',
    'ci_high nns',
    'iq_high nns',
    'median nns',
    'iq_low nns',
    'ci_low nns',
    'ci_high additional_tests',
    'iq_high additional_tests',
    'median additional_tests',
    'iq_low additional_tests',
    'ci_low additional_tests'
  )

library(reshape2)
library(tidyr)
ir_melt <- melt(ir_summary, id.vars = c('site', 'interv'))
ir_melt_sep <- separate(ir_melt, col = 'variable', into = c('stat', 'variable'), sep = ' ')
ir_dcast <- dcast(ir_melt_sep, site + interv + variable ~ stat)

ir_merge <- merge(ir_dcast, intervention_descriptions, by.x = 'interv', by.y = 'shortnames', all.x = T)

ir_merge$names <- ordered(ir_merge$names, rev(intervention_descriptions$names))

ir_merge$variable <-
  sapply(ir_merge$variable, function(x)
  c(additional_tests = 'Additional Tests', cases_averted = 'Cases Averted', nns = 'Number Needed to Screen')[[x]])

upper_val_add_tests <- max(filter(ir_merge, variable == 'Additional Tests')[['ci_high']])
upper_val_cases_averted <- max(filter(ir_merge, variable == 'Cases Averted')[['ci_high']])

ggplot(filter(ir_merge, site == 'Baltimore', variable %in% c('Additional Tests', 'Cases Averted'), interv %in% empirical_interventions)) + 
  geom_boxplot(
    stat = 'identity',
    aes(
    x = names,
    ymax = 100*ci_high,
    upper = 100*iq_high,
    middle = 100*median,
    lower = 100*iq_low,
    ymin = 100*ci_low
    # fill = frequency
    )
    ) + 
  ggtitle("Intervention Outcomes in Baltimore", subtitle = "Interventions Based on Current Strategies") + 
  theme_bw() + 
  facet_wrap(~variable, scales = 'free_x') + 
  coord_flip()  +
  xlab("") + 
  expand_limits(y=0) + 
  theme(axis.title.x = element_text(hjust = 1)) + 
  ylab("Additional Tests and Cases Averted as a Percentage of the Base Case")

ggsave("~/Documents/gcRegional/output/10-29-18/intervention_analysis_plots/intervention_outcomes_tests_ca_ba_empirical.png",
height = unit(6, 'in'), width = unit(9, 'in'))

ggplot(
  filter(
  ir_merge,
  site == 'Baltimore',
  variable %in% c('Additional Tests', 'Cases Averted'),
  !interv %in% empirical_interventions
  )
  ) + 
  geom_boxplot(
    stat = 'identity',
    aes(
    x = names,
    ymax = 100*ci_high,
    upper = 100*iq_high,
    middle = 100*median,
    lower = 100*iq_low,
    ymin = 100*ci_low
    # fill = frequency
    )
    ) + 
  ggtitle("Intervention Outcomes in Baltimore", subtitle = "Hypothetical Interventions") + 
  theme_bw() + 
  facet_wrap(~variable, scales = 'free_x') + 
  coord_flip()  +
  xlab("") + 
  expand_limits(y=0) + 
  theme(axis.title.x = element_text(hjust = 1)) + 
  ylab("Additional Tests and Cases Averted as a Percentage of the Base Case")


ggsave("~/Documents/gcRegional/output/10-29-18/intervention_analysis_plots/intervention_outcomes_tests_ca_ba_hypothetical.png",
height = unit(6, 'in'), width = unit(9, 'in'))


ggplot(filter(ir_merge, site == 'San Francisco', variable %in% c('Additional Tests', 'Cases Averted'), interv %in% empirical_interventions)) + 
  geom_boxplot(
    stat = 'identity',
    aes(
    x = names,
    ymax = 100*ci_high,
    upper = 100*iq_high,
    middle = 100*median,
    lower = 100*iq_low,
    ymin = 100*ci_low
    )
    ) + 
  ggtitle("Intervention Outcomes in San Francisco", subtitle = "Interventions Based on Current Strategies") + 
  theme_bw() + 
  facet_wrap(~variable, scales = 'free_x') + 
  coord_flip()  +
  xlab("") + 
  expand_limits(y=0) + 
  theme(axis.title.x = element_text(hjust = 1)) + 
  ylab("Additional Tests and Cases Averted as a Percentage of the Base Case")

ggsave("~/Documents/gcRegional/output/10-29-18/intervention_analysis_plots/intervention_outcomes_tests_ca_sf_empirical.png", height = unit(6, 'in'), width = unit(9, 'in'))

ggplot(filter(ir_merge, site == 'San Francisco', variable %in% c('Additional Tests', 'Cases Averted'), ! interv %in% empirical_interventions)) + 
  geom_boxplot(
    stat = 'identity',
    aes(
    x = names,
    ymax = 100*ci_high,
    upper = 100*iq_high,
    middle = 100*median,
    lower = 100*iq_low,
    ymin = 100*ci_low
    )
    ) + 
  ggtitle("Intervention Outcomes in San Francisco", subtitle = "Hypothetical Interventions") + 
  theme_bw() + 
  facet_wrap(~variable, scales = 'free_x') + 
  coord_flip()  +
  xlab("") + 
  expand_limits(y=0) + 
  theme(axis.title.x = element_text(hjust = 1)) + 
  ylab("Additional Tests and Cases Averted as a Percentage of the Base Case")

ggsave("~/Documents/gcRegional/output/10-29-18/intervention_analysis_plots/intervention_outcomes_tests_ca_sf_hypothetical.png", height = unit(6, 'in'), width = unit(9, 'in'))

```
