---
title: Simulating Intervention Scenarios
---

In order to simulate intervention scenarios we 
change the screening matrix used over the 2018-2023 
time period. In doing so, our simulations are altered to forecast 
the outcomes of two kinds of intervention scenarios:
Demographic targeted interventions, and interventions
where Loss-to-Follow-Up and Delay to treatment are
removed. 

First, we need our fit models and their projections over 2010 - 2023 as
our base case.

```{r, cache=T}
library(gcRegional)
library(ggplot2)

# Change the settings for screening trends which are only increasing logistic curves.
gc_testing <- c('logistic_screening', 'only_increasing_screening')

# Configure the model for Baltimore:
load_start("BA")

# Load model fit:
post.sample <- readRDS("~/Documents/gc-regional-project/data/2018-07-11-gcR-BA-calibration/post_sample.rds")

# post.sample has an mcmc chain of parameter vectors and the model simulations
# which correspond each row of parameter values.
summary(post.sample)

# In order to be able to work with this in this document, I'm going to take a
# sample of only 10 to work with by hand on my computer.

trace <- as.data.frame(post.sample$theta.list)
trace.burn.thin <- trace

# post.sample <- model_fits(trace.burn.thin, 20)
# pred <- as.data.frame(post.sample$outputs)
pred <- NULL
trace.sample <- trace[sample.int(nrow(trace), 10), ]
for (i in seq(nrow(trace.sample))) {
  res <- prediction_epi(unlist(trace.sample[i, ]), interv = "base_case")
  pred <- rbind.data.frame(unlist(res), pred)
}
colnames(pred) <- names(unlist(res))
```


```{r}
# This is when we could run plot_posteriors.
# plot_posteriors(output_directory = "~/Desktop/")

# Now I'd like to try and run the model for a longer forecast. 
gc_env$model.end <- gc_env$model.end + 5
gc_env$cal.end <- gc_env$cal.end + 5
```

```{r compute avg prevalence, cache = T}
out <- tidy_prevalence_dfs_for_many_simulations(
  trace_sample = trace.sample,
  ijkl_subset = c('l', 'j', 'i'), # excluding k because that's the "Low/High" risk group
  relative = F,
  years = 2010:2021,
  interv = 'base_case')

avg_prevalence <- average_tidy_prevalence_dfs(out)

#' summarize_prevalence's 
summarize_prevalence <- function(prevalence) {
  avg_burden <- prevalence[[1]]
  for (j in 1:nrow(prevalence[[1]])) {
    avg_burden[j, 4] <-
      mean(sapply(1:length(prevalence), function(i)
        prevalence[[i]][j, 4]), na.rm = T)
  }
  return(avg_burden)
}

prev_as_nested_sim_df <- function(prev) {
  a <- data.frame(sim = 1:length(prev))
  # remove the sim column from each df since it's just duplicated ints... 
  prev <- lapply(1:length(prev), function(x) dplyr::select(prev[[x]], -sim))
  a$data <- prev
  return(a)
}

prev <- prev_as_nested_sim_df(out)
avg_prev <- prev$data[[1]][, c('year', 'demographic')]
avg_prev$mean <- sapply(1:nrow(avg_prev), function(x) {
  mean(
    sapply(seq_along(prev$sim), function(y) prev$data[[y]][x, 'value'])
  )})
avg_prev$ci_high <- sapply(1:nrow(avg_prev), function(x) {
  quantile(
    x = sapply(seq_along(prev$sim), function(y) prev$data[[y]][x, 'value']),
    probs = .975
  )})
avg_prev$ci_low <- sapply(1:nrow(avg_prev), function(x) {
  quantile(
    x = sapply(seq_along(prev$sim), function(y) prev$data[[y]][x, 'value']),
    probs = .025
  )})
```

```{r split the demographic column}
avg_prev <- tidyr::separate(avg_prev, demographic, into = c('age', 'sex', 'race'), remove=F)
avg_prev <- tidyr::unite(avg_prev, col = 'racesex', race, sex, remove = F, sep=' ')
```

```{r visualize avg prevalence, cache=T}
p <- 
  ggplot(
    data = avg_prev,
    mapping = aes(
      x = year + 2009,
      y = mean,
      ymax = ci_high,
      ymin = ci_low,
      fill = demographic,
      color = demographic
      )) +
  geom_ribbon(alpha=0.4, size = 0) +  
  geom_line() +  
  ggtitle(
    paste0(
      "Projected Number of Infected Individuals in ",
      switch(gc_env$site, SF = "San Francisco", BA = "Baltimore")
    )
  ) +
  xlab("Year") +
  ylab("Number of Infected Individuals") +
  facet_wrap(~racesex) + 
  theme(
    axis.text.x = element_text(angle = 90),
    legend.position = 'bottom',
    legend.text = element_text(size = 10)
  )

print(p)

ggsave(p, filename = '~/Documents/gc-regional-project/outputs/2018-07-21/number_of_prevalent_cases.png', dpi = 300, width = unit(10, 'in'))
```



# Now let's try interventions

```{r MSM_annual intervention, cache=T}
out <- tidy_prevalence_dfs_for_many_simulations(
  trace_sample = trace.sample,
  ijkl_subset = c('l', 'j', 'i'), # excluding k because that's the "Low/High" risk group
  relative = F,
  years = 2010:2021,
  interv = 'remove_ltfu_and_delay_3week_20pct')

prev <- prev_as_nested_sim_df(out)

prev_with_ci <- function(prev) {
  avg_prev <- prev$data[[1]][, c('year', 'demographic')]
  avg_prev$mean <- sapply(1:nrow(avg_prev), function(x) {
    mean(
      sapply(seq_along(prev$sim), function(y) prev$data[[y]][x, 'value'])
    )})
  avg_prev$ci_high <- sapply(1:nrow(avg_prev), function(x) {
    quantile(
      x = sapply(seq_along(prev$sim), function(y) prev$data[[y]][x, 'value']),
      probs = .975
    )})
  avg_prev$ci_low <- sapply(1:nrow(avg_prev), function(x) {
    quantile(
      x = sapply(seq_along(prev$sim), function(y) prev$data[[y]][x, 'value']),
      probs = .025
    )})
  # split up the 'demographic' 
  avg_prev <- tidyr::separate(avg_prev, demographic, into = c('age', 'sex', 'race'), remove=F)
  avg_prev <- tidyr::unite(avg_prev, col = 'racesex', race, sex, remove = F, sep=' ')

  return(avg_prev)
}

avg_prev <- prev_with_ci(prev)

plot_prevalent_cases <- function(avg_prev, subtitle = NULL) {
  p <- 
  ggplot(
    data = avg_prev,
    mapping = aes(
      x = year + 2009,
      y = mean,
      ymax = ci_high,
      ymin = ci_low,
      fill = demographic,
      color = demographic
      )) +
  geom_ribbon(alpha=0.4, size = 0) +  
  geom_line() +  
  ggtitle(
    paste0(
      "Projected Number of Infected Individuals in ",
      switch(gc_env$site, SF = "San Francisco", BA = "Baltimore")
    ),
    subtitle = ifelse(is.null(subtitle), NULL, subtitle)
  ) +
  xlab("Year") +
  ylab("Number of Infected Individuals") +
  facet_wrap(~racesex) + 
  theme(
    axis.text.x = element_text(angle = 90),
    legend.position = 'bottom',
    legend.text = element_text(size = 10)
  )

  return(p)
}

p <- plot_prevalent_cases(avg_prev, subtitle = 'Projections with 3 Week Treatment Delay and 20% LTFU Removed')
print(p)

ggsave(p, filename = '~/Documents/gc-regional-project/outputs/2018-07-21/remove_ltfu_3week_20pct_prevalent_cases.png', dpi = 300, width = unit(10, 'in'), height = unit(7, 'in'))

```

