---
title: analyzing intervention simulation outcomes
output: html_document
---

We have simulated a variety of scenarios and now would 
like to analyze the outcomes from those simulations. 

First we load our simulation data. 

```{r get sim data, cache=T, echo=F}
devtools::load_all(".")
interventions_sf <- readRDS(system.file(package = 'gcRegional', 'intervention_simulations/interventions_data_SF.rds'))
interventions_ba <- readRDS(system.file(package = 'gcRegional', 'intervention_simulations/interventions_data_BA.rds'))
```

```{r print summary, cache=T}
names(interventions_ba)
unique(interventions_ba$variable)
```


The first plot I want to create is the following: 


| cases averted | number needed to screen to avert one case (nns) | 
|--|--|
| (horizontal bar with boxplot) | (horizontal bar with boxplot) |


The formulas for these are: 

`cases averted = basecase infections - intervention infections`

`nns = additional tests / cases averted`

`additional tests = number of tests in intervention - base case number of tests`

It must be kept in mind that these must be for a specific parameter vector from
the sample from the posterior distribution reflecting the models fit. 

This is the data frame I'll construct next: 

| sim | site| cases averted | additional tests | nns | 
|--|--|--|--|--|
|(data)|(data)|(data)|(data)|(data)|

!!! I'm realizing that I really should have included ALL individuals as one of the 
populations in the outcomes. 

Also, we're going to make these units relative rather than absolute.


```{r compute intermediate values, cache=T}
interventions <- setdiff(unique(interventions_ba$interv), 'base_case')

results_data <- list()

interventions_ba_filtered <- interventions_ba[interventions_ba$year == max(interventions_ba$year) & 
                                       interventions_ba$variable %in% c('incident_cases', 'number_screened') & 
                                       interventions_ba$population %in% c('Male', 'Female'),]

interventions_sf_filtered <- interventions_sf[interventions_sf$year == max(interventions_sf$year) & 
                                       interventions_sf$variable %in% c('incident_cases', 'number_screened') & 
                                       interventions_sf$population %in% c('Male', 'Female'),]

for (site in c("SF", "BA")) {
  df <- switch(site, SF = interventions_sf_filtered, BA=interventions_ba_filtered)
  for (sim in 1:max(interventions_ba_filtered$sim)) {
    for (interv in interventions) {
      
      # compute necessary intermediate values
      # computing cases_averted
      male_cases_in_interv = df[df$sim == sim &
                                  df$variable == 'incident_cases' &
                                  df$interv == interv &
                                  df$year == max(df$year) & df$population == 'Male', 'value']
      female_cases_in_interv = df[df$sim == sim &
                                  df$variable == 'incident_cases' &
                                  df$interv == interv &
                                  df$year == max(df$year) & df$population == 'Female', 'value']
      male_cases_in_base_case = df[df$sim == sim &
                                  df$variable == 'incident_cases' &
                                  df$interv == 'base_case' &
                                  df$year == max(df$year) & df$population == 'Male', 'value']
      female_cases_in_base_case = df[df$sim == sim &
                                  df$variable == 'incident_cases' &
                                  df$interv == 'base_case' &
                                  df$year == max(df$year) & df$population == 'Female', 'value']
      
      cases_averted = ((male_cases_in_base_case + female_cases_in_base_case) - 
        (male_cases_in_interv + female_cases_in_interv)) / (male_cases_in_base_case + female_cases_in_base_case)
      
      # computing number of additional tests
      male_number_screened_in_interv = df[df$sim == sim &
                                  df$variable == 'number_screened' &
                                  df$interv == interv &
                                  df$year == max(df$year) & df$population == 'Male', 'value']
      female_number_screened_in_interv = df[df$sim == sim &
                                  df$variable == 'number_screened' &
                                  df$interv == interv &
                                  df$year == max(df$year) & df$population == 'Female', 'value']
      male_number_screened_in_base_case = df[df$sim == sim &
                                  df$variable == 'number_screened' &
                                  df$interv == 'base_case' &
                                  df$year == max(df$year) & df$population == 'Male', 'value']
      female_number_screened_in_base_case = df[df$sim == sim &
                                  df$variable == 'number_screened' &
                                  df$interv == 'base_case' &
                                  df$year == max(df$year) & df$population == 'Female', 'value']
      
      additional_screens <- ((male_number_screened_in_interv + female_number_screened_in_interv) - 
        (male_number_screened_in_base_case + female_number_screened_in_base_case)) / 
        (male_number_screened_in_base_case + female_number_screened_in_base_case)
      
      # nns
      # nns <- additional_screens / cases_averted
      
      results_data[[length(results_data)+1]] = 
        list(
          sim = sim,
          site = site,
          interv = interv,
          cases_averted = cases_averted, 
          additional_tests = additional_screens
          # nns = nns
        )
    }
  }
}

intervention_results <- do.call(rbind.data.frame, results_data)
saveRDS(intervention_results, file.path(system.file("intervention_simulations", package = 'gcRegional'), 'intervention_results.rds'))
```


```{r, cache = T}
intervention_results <- intervention_results[complete.cases(intervention_results), ]
```

```{r, summarize}
ir_summary <- group_by(intervention_results, site, interv) %>% 
  summarize(
    ci_high_cases_averted = quantile(cases_averted, .975),
    iq_high_cases_averted = quantile(cases_averted, .75),
    median_cases_averted = median(cases_averted),
    iq_low_cases_averted = quantile(cases_averted, .25),
    ci_low_cases_averted = quantile(cases_averted, .025),
    # ci_high_nns = quantile(nns, 0.975),
    # iq_high_nns = quantile(nns, 0.75),
    # median_nns = median(nns),
    # iq_low_nns = quantile(nns, 0.25),
    # ci_low_nns = quantile(nns, 0.025),
    ci_high_tests = quantile(additional_tests, 0.975),
    iq_high_tests = quantile(additional_tests, 0.75),
    median_tests = median(additional_tests),
    iq_low_tests = quantile(additional_tests, 0.25),
    ci_low_tests = quantile(additional_tests, 0.025)
  )

intervention_results$site <- ifelse(intervention_results$site == 'SF', 'San Francisco', 'Baltimore')
ir_summary$site <- ifelse(ir_summary$site == 'SF', 'San Francisco', 'Baltimore')

```

```{r plot cases averted by additional tests per intervention}
library(ggplot2)


ggplot(ir_summary) + 
  geom_boxplot(stat = 'identity', aes(x = interv, ymax = ci_high_cases_averted, upper = iq_high_cases_averted, middle = median_cases_averted, lower = iq_low_cases_averted, ymin = ci_low_cases_averted)) + 
  ggtitle("Number of Cases Averted After 5 Years by Intervention") + 
  geom_hline(yintercept = 0, linetype ='dashed', color = 'red', alpha = 0.5) +
  facet_wrap(~site) + 
  coord_flip()  
ggsave(file.path(system.file("intervention_simulations", package = 'gcRegional'), 'cases_averted.png'), width=unit(10, 'in'), height=unit(7,'in'), dpi=300)

# ggplot(ir_summary) + 
#   geom_boxplot(stat = 'identity', aes(x = interv, ymax = ci_high_nns, upper = iq_high_nns, middle = median_nns, lower = iq_low_nns, ymin = ci_low_nns)) + 
#   ggtitle("Number Needed to Screen to Avert 1 Case over 5 Years by Intervention") + 
#   facet_wrap(~site) + 
#   coord_flip() 
# ggsave(file.path(system.file("intervention_simulations", package = 'gcRegional'), 'nns_all.png'), width=unit(10, 'in'), height=unit(7,'in'), dpi=300)
# 
# ggplot(ir_summary) + 
#   geom_boxplot(stat = 'identity', aes(x = interv, ymax = ci_high_nns, upper = iq_high_nns, middle = median_nns, lower = iq_low_nns, ymin = ci_low_nns)) + 
#   ggtitle("Number Needed to Screen to Avert a Case over 5 Years by Intervention") + 
#   facet_wrap(~site) + 
#   scale_y_log10(c(1,4000)) +
#   coord_flip()

# ggsave(file.path(system.file("intervention_simulations", package = 'gcRegional'), 'nns_logscale.png'), width=unit(10, 'in'), height=unit(7,'in'), dpi=300)

library(ggrepel)


ggplot(filter(intervention_results, site == 'Baltimore'), aes(x=additional_tests, y=cases_averted, color = interv)) + 
  geom_point(alpha=0.5) +
  ggrepel::geom_label_repel(
    data = filter(ir_summary, site == 'Baltimore'),
    mapping = aes(
      group = interv,
      x = median_tests,
      y = median_cases_averted,
      label = interv),
    size = 3,
    alpha = 0.7
  ) +
  theme_bw() + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(), legend.position = 'none',
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
  geom_hline(yintercept = 0, color = 'red', linetype='dashed', alpha=0.8) + 
  ggtitle("Cases Averted Compared to Number of Additional Tests", subtitle = 'in Baltimore')

ggsave(file.path(system.file("intervention_simulations", package = 'gcRegional'), 'cases_averted_by_num_tests_ba.png'), width=unit(14, 'in'), height=unit(10,'in'), dpi=300)

ggplot(filter(intervention_results, site == 'San Francisco'), aes(x=additional_tests, y=cases_averted, color = interv)) + 
  geom_point(alpha=0.5) +
  ggrepel::geom_label_repel(
    data = filter(ir_summary, site == 'San Francisco'),
    mapping = aes(
      group = interv,
      x = median_tests,
      y = median_cases_averted,
      label = interv),
    size = 3,
    alpha = 0.7
  ) +
  theme_bw() + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(), legend.position = 'none',
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
  geom_hline(yintercept = 0, color = 'red', linetype='dashed', alpha=0.8) + 
  ggtitle("Cases Averted Compared to Number of Additional Tests", subtitle = 'in San Francisco')

ggsave(file.path(system.file("intervention_simulations", package = 'gcRegional'), 'cases_averted_by_num_tests_sf.png'), width=unit(14, 'in'), height=unit(10,'in'), dpi=300)


empirical_interventions <- c('remove_ltfu_10pct', 'remove_ltfu_20pct', 'remove_f_msm_10pct_and_msw_20pct_ltfu', '1year_high_activity_semi_annual')

ba_sf_cases_averted_by_additional_tests <- ggplot(filter(intervention_results, ! interv %in% empirical_interventions), aes(x=additional_tests, y=cases_averted, color = interv)) + 
  geom_point(alpha=0.5) +
  ggrepel::geom_label_repel(
    data = filter(ir_summary, ! interv %in% empirical_interventions),
    mapping = aes(
      group = interv,
      x = median_tests,
      y = median_cases_averted,
      label = interv),
    size = 3,
    alpha = 0.7
  ) +
  facet_wrap(~site) + 
  theme_bw() + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(), legend.position = 'none',
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
  geom_hline(yintercept = 0, color = 'red', linetype='dashed', alpha=0.8) + 
  ggtitle("Cases Averted Compared to Number of Additional Tests", subtitle = 'Relative to Base Case')

ggsave(ba_sf_cases_averted_by_additional_tests, file.path(system.file("intervention_simulations", package = 'gcRegional'), 'cases_averted_by_additional_tests.png'), width=unit(14, 'in'), height=unit(10,'in'), dpi=300)


ggplot(filter(intervention_results, interv %in% empirical_interventions), aes(x=additional_tests, y=cases_averted, color = interv)) + 
  geom_point(alpha=0.5) +
  ggrepel::geom_label_repel(
    data = filter(ir_summary, interv %in% empirical_interventions),
    mapping = aes(
      group = interv,
      x = median_tests,
      y = median_cases_averted,
      label = interv),
    size = 3,
    alpha = 0.7
  ) +
  facet_wrap(~site) + 
  theme_bw() + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(), legend.position = 'none',
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
  geom_hline(yintercept = 0, color = 'red', linetype='dashed', alpha=0.8) + 
  ggtitle("Cases Averted Compared to Number of Additional Tests", subtitle = 'Relative to Base Case')

ggsave(file.path(system.file("intervention_simulations", package = 'gcRegional'), 'cases_averted_by_additional_tests_empirical.png'), width=unit(14, 'in'), height=unit(10,'in'), dpi=300)


# 
#   ggplot(
#   filter(intervention_results,!interv %in% empirical_interventions),
#   aes(x = additional_tests, y = cases_averted, color = interv)
#   ) +
#   # geom_point(alpha=0.5) +
#   facet_wrap(~site) + 
#   geom_hline(
#     yintercept = 0,
#     color = 'red',
#     linetype = 'dashed',
#     alpha = 0.8
#     ) +
#     ggtitle("Cases Averted Compared to Number of Additional Tests", subtitle = 'Relative to Base Case') +
#   geom_density_2d(alpha=0.7) + 
#   ggrepel::geom_label_repel(
#     data = filter(ir_summary, ! interv %in% empirical_interventions),
#     mapping = aes(
#       group = interv,
#       x = median_tests,
#       y = median_cases_averted,
#       label = interv),
#     size = 3
#   ) + 
#   theme_bw() + 
#   theme(
#     panel.border = element_blank(),
#     panel.grid.major = element_blank(),
#     legend.position = 'none',
#     panel.grid.minor = element_blank(),
#     axis.line = element_line(colour = "black")
#     ) 
# 
# ggsave(file.path(system.file("intervention_simulations", package = 'gcRegional'), 'cases_averted_by_additional_tests_contours.png'), width=unit(14, 'in'), height=unit(10,'in'), dpi=300)
# 
# 
#   ggplot(
#   filter(intervention_results,!interv %in% empirical_interventions),
#   aes(x = additional_tests, y = cases_averted, color = interv)
#   ) +
#   # geom_point(alpha=0.5) +
#   facet_wrap(site~interv) + 
#   geom_hline(
#     yintercept = 0,
#     color = 'red',
#     linetype = 'dashed',
#     alpha = 0.8
#     ) +
#     ggtitle("Cases Averted Compared to Number of Additional Tests", subtitle = 'Relative to Base Case') +
#   geom_density_2d(alpha=0.7) + 
#   theme_bw() + 
#   theme(
#     panel.border = element_blank(),
#     panel.grid.major = element_blank(),
#     legend.position = 'none',
#     panel.grid.minor = element_blank(),
#     axis.line = element_line(colour = "black")
#     ) 
# 
# ggsave(file.path(system.file("intervention_simulations", package = 'gcRegional'), 'cases_averted_by_additional_tests_contours_by_interv.png'), width=unit(14, 'in'), height=unit(20,'in'), dpi=300)

```



```{r calculate prevalence}
results <- list()
for (site in c("SF", "BA")) {
  df <- switch(site, BA = interventions_ba, SF = interventions_sf)
  df <- filter(df, variable %in% c('population_size', 'asymptomatic_cases', 'symptomatic_cases'), population %in% c('Male', 'Female'))
for (interv in c(interventions, 'base_case')) { 
  interv_df <- filter(df, interv == interv)
for (sim in unique(interv_df[['sim']])) {
  sim_df <- filter(interv_df, sim == sim)
for (year in unique(sim_df[['year']])) {
  year_df <- filter(sim_df, year == year)
  
  # (male + female) (symptomatic + asymptomatic cases) / (male popsize + female popsize)
  male_symptomatic <- filter(year_df, population == 'Male', variable == 'symptomatic_cases')[['value']]
  female_symptomatic <-filter(year_df, population == 'Female', variable == 'symptomatic_cases')[['value']] 
  male_asymptomatic <- filter(year_df, population == 'Male', variable == 'asymptomatic_cases')[['value']]
  female_asymptomatic <-filter(year_df, population == 'Female', variable == 'asymptomatic_cases')[['value']] 
  
  male_popsize <-  filter(year_df, population == 'Male', variable == 'population_size')[['value']]
  female_popsize <-filter(year_df, population == 'Female', variable == 'population_size')[['value']] 
  
  prevalence <- (male_symptomatic + male_asymptomatic + female_symptomatic + female_asymptomatic) / (male_popsize + female_popsize)

  results[[length(results)+1]] <- 
    c( sim = sim,
       site = site,
       interv = interv,
       year = year,
       prevalence = prevalence
    )
}
} 
}
}

# next step: summarize -- and make sure that the years 
```


```{r calculate prevalence with dplyr}
df <- do.call(
  rbind, 
  list(
    cbind.data.frame(site = 'BA', filter(interventions_ba, variable %in% c('population_size', 'asymptomatic_cases', 'symptomatic_cases'), population %in% c('Male', 'Female'))),
    cbind.data.frame(site = 'SF', filter(interventions_sf, variable %in% c('population_size', 'asymptomatic_cases', 'symptomatic_cases'), population %in% c('Male', 'Female')))
  ))

df <- reshape2::dcast(df, site + sim + interv + year ~ variable + population, value.var = 'value')

summary_df <- group_by(df, site, sim, interv, year) %>% 
  summarize(
    prevalence = (
    symptomatic_cases_Male + symptomatic_cases_Female + 
      asymptomatic_cases_Male + asymptomatic_cases_Female
    ) / (population_size_Male + population_size_Female)
    )

ci_df <- group_by(summary_df, site, interv, year) %>% 
  summarise(mean = mean(prevalence, na.rm=T),
            ci_high = quantile(prevalence, 0.975, na.rm = T),
            ci_low = quantile(prevalence, 0.025, na.rm = T))

library(ggplot2)

ci_df$interv <- sapply(ci_df$interv, function(str) paste0(strwrap(gsub("_", " ", str), width = 15), collapse='\n'))

ggplot(ci_df, aes(x = year, y = mean, ymax = ci_high, ymin = ci_low, fill = interv, color = interv)) + 
  geom_ribbon(size = 0, alpha=0.5) + 
  geom_line() + 
  facet_grid(site ~ interv) + 
  theme(legend.position = 'none', axis.text.x = element_text(angle = 90)) + 
  scale_x_continuous(breaks = seq(min(ci_df$year), max(ci_df$year), by = 4))

ggsave(
  file.path(
  system.file("intervention_simulations", package = 'gcRegional'),
  "intervention_prevalence_absolute.png"
  ),
  dpi = 300,
  width = unit(14, 'in'),
  height = unit(7, 'in')
  )

summary_df_dcast <- dcast(summary_df, site + sim + year ~ interv)

library(magrittr)
for (interv in interventions) {
    summary_df_dcast[[interv]] = summary_df_dcast[[interv]] / summary_df_dcast[['base_case']]
}

summary_df_dcast %<>% select(-base_case)

relative_summary_df <- melt(summary_df_dcast, id.vars = c('site', 'sim', 'year'), variable.name = 'interv', value.name = 'prevalence')

relative_ci_df <- relative_summary_df %>%  
  group_by(site, interv, year) %>% 
  summarise(mean = mean(prevalence, na.rm = T), 
            ci_high = quantile(prevalence, 0.975, na.rm = T),
            iq_high = quantile(prevalence, 0.75, na.rm = T),
            ci_low = quantile(prevalence, 0.025, na.rm = T),
            iq_low = quantile(prevalence, 0.25, na.rm = T))
  
library(ggrepel)

last_data_points <- as.data.frame(do.call(
  rbind.data.frame,
  list(
    filter(relative_ci_df, site == 'BA', year == 2022),
    filter(relative_ci_df, site == 'SF', year == 2021)
  )))
                            
library(ggrepel)

ggplot(filter(relative_ci_df, year >= 2015), aes(x = year, y = mean, color = interv)) + 
  geom_ribbon(aes(ymax = ci_high, ymin = ci_low, fill = interv), alpha = 0.2, size = 0) + 
  geom_line() + 
  facet_wrap(~site) + 
  scale_x_continuous(
    breaks = seq(min(relative_ci_df$year), max(relative_ci_df$year), by = 1), 
    limits = c(2015, 2024)) +
  geom_label_repel(data = last_data_points, aes(x = year, y = mean, group = interv, label = interv), segment.color = 'black', segment.size = .5, segment.alpha = 0.5, nudge_x = 2.5, direction = 'y', size = 2) +
  theme(legend.position = 'none')

ggsave(file.path(
  system.file("intervention_simulations", package = 'gcRegional'),
  "intervention_prevalence_relative.png"
  ),
  dpi = 300,
  width = unit(14, 'in'),
  height = unit(7, 'in')
  )


ggplot(
  last_data_points,
  aes(
  x = interv,
  middle = mean,
  ymax = ci_high,
  ymin = ci_low,
  upper = iq_high,
  lower = iq_low,
  fill = interv
  ),
  alpha = 0.5
  ) + 
  geom_boxplot(stat = 'identity') + 
  facet_wrap(~site) + 
  coord_flip() + 
  theme_bw() + 
  theme(legend.position = 'none') + 
  ggtitle("Prevalence in Last Intervention Year Compared to Base Case")

ggsave("~/Documents/gcRegional/output/10-29-18/intervention_analysis_plots/prevalence_ratio_in_last_year.png", height = unit(5, 'in'), width = unit(9, 'in'))


```
